### 2019-08-09 paper/ms.tex
Initial commit

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

\newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
\newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
\newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[The Transition Redshift]{The transition redshift as a probe of reionization}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. Beane and K. Moriwaki]{
Angus Beane$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu}
and Kana Moriwaki$^{2}$\thanks{E-mail: kana.moriwaki@utap.phy.s.u-tokyo.ac.jp}
\\
% List of institutions
$^{1}$Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
$^{2}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan
% $^{2}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA\\
% $^{3}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2019}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
The early stages of the Epoch of Reionization (EoR), probed by the 21~cm line,
are sensitive to the detailed formation of the first galaxies. An important
transition occurs on large scales at $\avg{x_i}\sim0.15$, when the 21~cm field
transitions from being positively correlated with the galaxy field to being
negatively correlated. The redshift at which this transition occurs (the
``transition redshift'') is, in principle, sensitive to both the structure of
the 21~cm field but also the galaxy field. However, by considering a fixed
model for the EoR and varying the parameters of a simple model for the galaxy
field in a mock [O~\textsc{iii}]-emitter sample cross-correlation, we show
that the transition redshift is in fact insensitive to the structure of the
selected galaxy sample. We show that prospects for measuring the transition
redshift are feasible in the near-term with a combination of LOFAR and JWST.
Being derived from a cross-correlation, the transition redshift is less
impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
measurements. Therefore, the transition redshift is a promising probe of the
early stages of the EoR.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
cosmology: theory -- dark ages, reionization, first stars -- large-scale
structure of Universe
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}
The introduction.

\section{Conclusions}

The conclusions.

\section*{Acknowledgements}

The Acknowledgements section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

\appendix

\section{Some extra material}

The appendix.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2019-08-09 paper/ms.tex
Add beginning of intro

@@
 \section{Introduction}
-The introduction.
+The redshifted 21~cm line contains a great deal of information about the
+structure and evolution of the Epoch of Reionization (EoR). Once measured at
+$z\sim6\textup{--}12$, it should reveal the nature of the formation of the
+first stars, galaxies, and black holes, as well as the large-scale structure
+of the Universe at high redshift \citep{2013fgu..book.....L}. While
+instruments have reached the sensitivity necessary to detect the signal during
+the EoR, issues of foreground contamination and instrumental artifacts have so
+far prevented the success of such efforts. Only upper limits have been placed
+on the amplitude of the 21~cm fluctuations \citep[e.g.][]{2013MNRAS.433..639P,
+2014PhRvD..89b3002D, 2016ApJ...833..102B, 2017ApJ...838...65P}.
 

### 2019-08-09 paper/ms.tex
Add section on papers to cite

@@
 
+\section{To cite}
+Papers that need to be cited:
+
+The Cross-Correlation of High-Redshift 21 cm and Galaxy Surveys
+\url{https://arxiv.org/abs/astro-ph/0611274}
+
+Probing Reionization with the 21 cm-Galaxy Cross Power Spectrum
+\url{https://arxiv.org/abs/0806.1055}
+
+The HI Bias during the Epoch of Reionization, discusses the positive/negative
+correlation transition as a function of $k$
+\url{https://arxiv.org/abs/1907.05098}
+
 \section{Conclusions}

### 2019-08-09 paper/ms.tex
Small changes
Add beginning of methods section

@@
 
+\newcommand{\tfast}{\texttt{21cmFAST}}
+
 \newcommand{\avg}[1]{\ensuremath{\langle #1 \rangle}}
@@
 % Keep the title short and informative.
-\title[The Transition Redshift]{The transition redshift as a probe of reionization}
+\title[The transition redshift]{The transition redshift as a probe of reionization}
 
@@
 
+\section{Methods}
+\subsection{21cmFAST}
+We generate realizations of the 21~cm field for our different EoR models using
+the publicly available code \tfast{}
+v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST},
+commit: \texttt{42e7566}}. Spin temperature fluctuations are computed and the
+excursion set approach is used to identify the ionized regions
+\citep{2011MNRAS.411..955M}.
+
 \section{To cite}
@@
 
-%\bibliographystyle{mnras}
-%\bibliography{example} % if your bibtex file is called example.bib
+\bibliographystyle{mnras}
+\bibliography{references} % if your bibtex file is called example.bib
 

### 2019-08-11 paper/ms.tex
Add some commands
Update short title
Slightly modify abstract

@@
 
+\newcommand{\beq}{\begin{equation}}
+\newcommand{\eeq}{\end{equation}}
+
 \newcommand{\tfast}{\texttt{21cmFAST}}
@@
 \newcommand{\CII}{\ensuremath{\text{C~\textsc{ii}}}}
+\newcommand{\HII}{\ensuremath{\text{H~\textsc{ii}}}}
 \newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
+
+\newcommand{\Msun}{\ensuremath{\text{M}_\odot}}
+\newcommand{\kpc}{\ensuremath{\text{kpc}}}
+\newcommand{\Mpc}{\ensuremath{\text{Mpc}}}
+\newcommand{\Myr}{\ensuremath{\text{Myr}}}
+\newcommand{\Gyr}{\ensuremath{\text{Gyr}}}
+\newcommand{\kms}{\ensuremath{\text{km}\,\text{s}^{-1}}}
+
+\newcommand{\fid}{\texttt{fid}}
+\newcommand{\hot}{\texttt{hot}}
+\newcommand{\cold}{\texttt{cold}}
 
@@
 % Keep the title short and informative.
-\title[The transition redshift]{The transition redshift as a probe of reionization}
+\title[The transition redshift as an EoR probe]{The transition redshift as a probe of reionization}
 
@@
 impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
-measurements. Therefore, the transition redshift is a promising probe of the
-early stages of the EoR.
+measurements. Therefore, the transition redshift is an interesting probe of
+the early stages of the EoR, and its detectability and interpretability
+deserve further study.
 \end{abstract}

### 2019-08-11 paper/ms.tex
Add lot more to intro

@@
 
-\section{Introduction}
+\section{Introduction} \label{sec:intro}
 The redshifted 21~cm line contains a great deal of information about the
@@
 
-\section{Methods}
-\subsection{21cmFAST}
+Because of the great difficulties confronting 21~cm auto-spectrum
+measurements, the prospect of measuring 21~cm in cross-correlation with
+another tracer of large-scale structure, such as galaxies. The galaxy field
+will only correlate with the cosmological 21~cm signal, and the foregrounds
+will not contribute to the mean signal (though they will make the measurement
+noisy, and so some foreground subtraction is still necessary).
+
+The 21~cm-galaxy cross-correlation was first explored by
+\citet{2007MNRAS.375.1034W} in the context of using Ly$\alpha$-emitters to
+distinguish between ``inside-out'' and ``outside-in'' reionization scenarios.
+However, this technique is limited to the late stages of reionization since
+Ly$\alpha$-emitters are obscured by neutral hydrogen even slightly earlier
+into the EoR \citep[e.g.][]{2006ApJ...648....7K}. \citet{2007ApJ...660.1030F}
+expanded upon this by considering a general galaxy survey. It was later shown
+that the scale at which the cross-correlation goes from negative to zero (the
+``turnover scale'') provides a tracer of the bubble size. However, the precise
+turnover scale also depends on the properties of the selected galaxy sample,
+with turnover happening on larger scales if only more massive galaxies can be
+detected \citep{2009ApJ...690..252L}. A number of authors have studied this
+cross-correlation in the context of detectability of the anti-correlation on
+large scales \citep{2013MNRAS.432.2615W, 2016MNRAS.457..666V,
+2017ApJ...836..176H}, and its dependence on the details of the EoR
+\citep{2014MNRAS.438.2474P}.
+
+In addition to the cross-correlation between 21~cm and galaxies, the
+cross-correlation between 21~cm and intensity maps has been investigated in an
+analogous fashion. Line intensity mapping experiments aim to measure the
+large-scale structure of emission in a certain line, and is easier to perform
+over a large area at high redshift than a galaxy survey. Current targets
+include [\CII], CO, Ly$\alpha$, and H$\alpha$ \citep[for a recent review,
+see][]{2017arXiv170909066K}. Another intriguing possible line is [\OIII]
+$88\,\mu \text{m}$ \citep[e.g.][]{2018MNRAS.481L..84M}, in which a lensed
+$z=9.1$ galaxy has recently shown to be exceptionally bright
+\citep{2018Natur.557..392H}.
+
+This cross-correlation was first studied with the CO rotational lines
+\citep{2011ApJ...741...70L}, and then the [\CII] \citep{2012ApJ...745...49G}
+and Ly$\alpha$ lines \citep{2013ApJ...763..132S}. The possibility of using the
+cross-bispectrum the 21~cm and [\CII] fields has been explored
+\citep{2018ApJ...867...26B}, along with combining the three cross-spectra with
+a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. While in
+this work we will only consider the cross-correlation between 21~cm and
+galaxies, all of what we consider is applicable to the transition redshift as
+computed by cross-correlating 21~cm with any of these emission lines.
+
+In the case of either galaxies or emission lines, it is expected that the two
+are positively correlated at the very beginning of the EoR (though the
+emission lines may be very weak due to the lack of significant metal
+enhancement). This is because the densest regions host the most mass and
+therefore 21~cm emission and galaxy populations. However, the densest regions
+will also ionize first {\bf cite something}, and after some time 21~cm and
+galaxies will become negatively correlated. We refer to the redshift at which
+this transition occurs at a fixed $k$ as the ``transition redshift''
+$z_\star(k)$, assuming that only one such zero exists. In other words, the
+cross-correlation at $k$ vanishes at $z=z_{\star}(k)$.
+
+In this work we investigate to what extent the transition redshift is
+dependent upon the galaxy sample used to define it. We assume a galaxy catalog
+selected using an [\OIII] emitter survey. In particular, we are interested in
+how $z_\star$ changes as we vary the parameters of the [\OIII] luminosity-mass
+relation for a fixed halo catalog.
+
+\section{Methods} \label{sec:methods}
+\subsection{21cmFAST} \label{ssec:tfast}
 We generate realizations of the 21~cm field for our different EoR models using

### 2019-08-11 paper/ms.tex
Add more info about 21cmFAST runs

@@
 the publicly available code \tfast{}
-v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST},
-commit: \texttt{42e7566}}. Spin temperature fluctuations are computed and the
+v1.3\footnote{\url{https://github.com/andreimesinger/21cmFAST}, commit:
+\texttt{42e7566}}. Spin temperature fluctuations are computed and the
 excursion set approach is used to identify the ionized regions
-\citep{2011MNRAS.411..955M}.
+\citep{2011MNRAS.411..955M}. Rather than using the mean collapsed fraction, we
+use the halo field to compute the ionization and 21~cm fields, since we are
+interested in the evolution at early redshifts where the Poisson statistics of
+the halo field can be important.
+
+The parameters used in our \tfast{} runs are as folows. The minimum halo mass
+contributing to the ionizing budget is $10^{8}\,\Msun$. The \HII{} efficiency
+factor ($\zeta$) is set to $10$. The maximum smoothing scale for the
+ionization field $R_{\text{max}}$ (loosely referred to as the ``mean-free
+path'') is set to $30\,\Mpc$, though this quantity has almost no effect on the
+early stage of the EoR. We set the fraction of baryons converted to stars
+($f_\star$) to be $0.1$. We ignore redshift-space distortions for convenience.
+All other parameters are set to their default values, except for the heating
+parameter discussed in the next paragraph. The exact parameter files are given
+in the github repository associated with this work (see the Supplementary
+Material).
+
+Our three different models for the EoR differ in the efficiency of their
+heating, controlled by the number of X-ray photons per solar mass in galaxies
+($\zeta_X$). Our fiducial model (\fid{}) is the default value
+$\zeta_X=2\times10^{56}$, while our ``hot'' and ``cold'' models (\hot{} and
+\cold{}) set $\zeta_X=10^{57}$ and $5\times10^{55}$, respectively. The average
+$\delta T_b$ signal is shown in \textbf{some figure}, which shows
+\textbf{something}. Note that none of these models account for the recent
+claimed detection by the EDGES group of an extremely deep absorption trough at
+$z\sim17$ \citep{2018Natur.555...67B}. If confirmed, though, that detection
+would indicate an extremely low gas temperature at $z\sim17$, which would
+favor larger amplitudes of the spin temperature fluctuations at $z\sim10$,
+unless heating were extremely efficient after $z\sim17$. {\bf don't know how I
+feel about the last sentence}
 

### 2019-08-11 paper/ms.tex
Add beginning of OIII lum sec

@@
 
+\subsection{[\OIII] luminosity} \label{ssec:oiii_lum}
+
+In order to model the relation between [\OIII] luminosity ($L_{\OIII}$) and
+halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
+the luminosity for halo $j$
+\beq \label{eq:lum_mass_relation}
+L_j(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha} + s_j(w)
+\eeq
+where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
+[\OIII] at that redshift, $\alpha$ is the power-law index, and $s_j(w)$ is a
+number randomly selected from a lognormal distribution with zero mean and
+width $w$. Once the average intensity is fixed (which we assume so), this is a
+two-parameter model ($\alpha$ and $w$) of the [\OIII] luminosity-mass
+relation.
+
+\section{Detectability}
+
 \section{To cite}
@@
 
-\section{Conclusions}
+\section{Conclusions} \label{sec:conclusions}
 

### 2019-08-11 plots/helper.py
Write helper functions for reading xps, finding ztran

@@ -1,0 +1,44 @@
+import glob
+import numpy as np
+import re
+from scipy.interpolate import interp1d
+from scipy.optimize import ridder
+
+h = 0.6766
+
+def read_xps(directory):
+    directory = directory+'/xps*'
+    xps_list = glob.glob(directory)
+    print(directory)
+    zlist = np.array([float(re.findall('\d\d\d\.\d\d', f)[0]) for f in xps_list])
+    
+    output = []
+    for i,key in enumerate(np.argsort(zlist)):
+        fname = xps_list[key]
+        data = np.genfromtxt(fname)
+        xps = data[:,3]
+        output.append(xps)
+        if i ==0:
+            klist = data[:,0]/h
+    
+    zlist = np.sort(zlist)
+
+    output = np.array(output)
+    return zlist, klist, output
+
+def find_ztran(zlist, klist, xps):
+    ztran = []
+    for k in range(len(klist)):
+        this_xps = xps[:,k]
+        
+        xps_fn_z = interp1d(zlist, this_xps)
+        try:
+            sol = ridder(xps_fn_z, 9, 16)
+        except:
+            sol = np.nan
+        print(sol)
+        this_ztran = float(sol)
+        ztran.append(this_ztran)
+
+    return klist, np.array(ztran)
+

### 2019-08-11 plots/ztran_vs_k/plot_ztran_vs_k.py
Create ztran vs. k plot

@@ -1,0 +1,51 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+import sys
+sys.path.append('../')
+from helper import *
+
+import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.ticker import FormatStrFormatter
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath} \usepackage{bm}']
+
+textwidth = 7.10000594991
+columnwidth = 3.35224200913
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+base_dir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
+fid_dir = base_dir + '/fid' + '/MyOutput'
+cold_dir = base_dir + '/cold' + '/MyOutput'
+hot_dir = base_dir + '/hot' + '/MyOutput'
+dir_list = [hot_dir, fid_dir, cold_dir]
+name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
+color_list = [tb_c[1], tb_c[-1], tb_c[3]]
+
+fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
+
+for name, directory, c in zip(name_list, dir_list, color_list):
+    zlist, klist, xps = read_xps(directory)
+    klist, ztran = find_ztran(zlist, klist, xps)
+
+    ax.plot(klist, ztran, label=name, c=c)
+
+ax.set_xscale('log')
+
+ax.set_xlim(0.1, 1.0)
+ax.set_ylim(9, 12)
+
+ax.set_xlabel(r'$k\,[\,h\text{Mpc}^{-1}\,]$')
+ax.set_ylabel(r'$z_{\star}$')
+
+ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
+ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
+
+ax.legend(title='model', frameon=False)
+fig.tight_layout()
+
+fig.savefig('ztran_vs_k.pdf')

### 2019-08-11 plots/helper.py
Update helper.py

@@ -6,10 +6,8 @@ from scipy.optimize import ridder
 
 h = 0.6766
 
-def read_xps(directory):
-    directory = directory+'/xps*'
-    xps_list = glob.glob(directory)
-    print(directory)
+def read_xps(files):
+    xps_list = glob.glob(files)
     zlist = np.array([float(re.findall('\d\d\d\.\d\d', f)[0]) for f in xps_list])
     
     output = []
@@ -42,3 +40,56 @@ def find_ztran(zlist, klist, xps):
 
     return klist, np.array(ztran)
 
+def gen_halo_catalog(fin, fout, n, Mcut=None):
+    t = np.genfromtxt(fin)
+
+    if Mcut is not None:
+        keys = np.where(t[:,0] > Mcut)[0]
+        t = t[keys]
+
+    poslist = t[:,1:4]
+    pos_in_n = (poslist*n).astype('int')
+
+    ng = np.histogramdd(pos_in_n, bins=(n,n,n))[0]
+    aven = np.mean(ng)
+    ng = np.divide(np.subtract(ng, aven), aven)
+
+    ng = ng.astype('f4')
+    ng.tofile(fout)
+
+def read_file(fname, npix, reshape=True):
+    data = np.fromfile(fname, dtype='f4')
+    assert len(data) == npix**3, "Data is not right length for number of specified pixels"
+
+    if reshape:
+        return np.reshape(data, (npix, npix, npix))
+    else:
+        return data
+
+def compute_power_spectrum(field, Lbox, npix, kmin=None, kmax=None, deltak=1.4):
+    if kmin is None:
+        kmin=2.*np.pi/Lbox
+    if kmax is None:
+        kmax=kmin*npix
+
+    bins = [kmin]
+    while bins[-1] <= kmax:
+        bins.append(bins[-1]*deltak)
+
+    volume = Lbox**3
+    tot_npix = npix**3
+
+    field_ft = np.fft.fftn(field)
+    k1d = np.fft.fftfreq(npix, d=Lbox/npix)
+
+    kx, ky, kz = np.meshgrid(k1d, k1d, k1d, indexing='ij')
+    kmag = np.sqrt(np.square(kx) + np.square(ky) + np.square(kz))
+
+    kmag_1d = np.reshape(kmag, npix**3)
+    field_ft_1d = np.reshape(field_ft, npix**3)
+
+    Nlist = np.histogram(kmag_1d, bins)[0]
[…]

### 2019-08-11 scripts/run_halo_gen.py
Create run_halo_gen.py

@@ -1,0 +1,29 @@
+import numpy as np
+import glob
+from tqdm import tqdm
+
+import sys
+sys.path.append('../plots/')
+from helper import *
+
+basedir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
+fid_dir = basedir + '/fid'
+cold_dir = basedir + '/cold'
+hot_dir = basedir + '/hot'
+dir_list = [hot_dir, fid_dir, cold_dir]
+
+Mcut_list = [1E9, 1E10, 1E11]
+Mcut_list_label =['Mcut1e9','Mcut1e10','Mcut1e11']
+
+for directory in dir_list:
+    fin_directory = directory + '/Output_files/Halo_lists'
+    fout_directory = directory + '/MyOutput'
+
+    for fin in tqdm(glob.glob(fin_directory+'/halos*')):
+
+        z = float(re.findall('\d?\d\.\d\d', fin)[0])
+        zlabel = "{:06.2f}".format(z)
+
+        for Mcut,label in zip(Mcut_list,Mcut_list_label):
+            fout = fout_directory+'/halos_z'+zlabel+'_'+label
+            gen_halo_catalog(fin, fout, 256, Mcut=Mcut)

### 2019-08-11 plots/ztran_vs_k/plot_ztran_vs_k.py
Fix plot_ztran_vs_k.py

@@ -29,7 +29,7 @@ color_list = [tb_c[1], tb_c[-1], tb_c[3]]
 fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
 
 for name, directory, c in zip(name_list, dir_list, color_list):
-    zlist, klist, xps = read_xps(directory)
+    zlist, klist, xps = read_xps(directory+'/xps*')
     klist, ztran = find_ztran(zlist, klist, xps)
 
     ax.plot(klist, ztran, label=name, c=c)

### 2019-08-11 plots/xps_vs_z/plot_xps_z.py
Create xps vs z plot

@@ -1,0 +1,59 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+import sys
+sys.path.append('../')
+from helper import *
+
+import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.ticker import FormatStrFormatter
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath} \usepackage{bm}']
+
+textwidth = 7.10000594991
+columnwidth = 3.35224200913
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+base_dir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
+fid_dir = base_dir + '/fid' + '/MyOutput'
+cold_dir = base_dir + '/cold' + '/MyOutput'
+hot_dir = base_dir + '/hot' + '/MyOutput'
+dir_list = [hot_dir, fid_dir, cold_dir]
+name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
+color_list = [tb_c[1], tb_c[-1], tb_c[3]]
+
+Mcut_list = [1E9, 1E10, 1E11]
+Mcut_list_label =['Mcut1e9','Mcut1e10','Mcut1e11']
+ls_list = ['solid', 'dashed', 'dotted']
+
+fig, ax = plt.subplots(1, 1, figsize=(textwidth, columnwidth))
+
+for name, directory, c in zip(name_list, dir_list, color_list):
+    for i,(label, ls) in enumerate(zip(Mcut_list_label, ls_list)):
+        zlist, klist, xps = read_xps(directory+'/halo_xps/*'+label+'*.txt')
+        klist, ztran = find_ztran(zlist, klist, xps)
+        if i==0:
+            ax.plot(zlist, xps[:,3], label=name, c=c, ls=ls)
+        else:    
+            ax.plot(zlist, xps[:,3], c=c, ls=ls)
+
+# ax.set_xscale('log')
+ax.set_yscale('symlog')
+
+ax.set_xlim(9, 14)
+ax.set_ylim(-1e6, 1e6)
+
[…]

### 2019-08-11 plots/aveTb/plot_aveTb.py
Add avetb plot

@@ -1,0 +1,57 @@
+import numpy as np 
+import glob
+
+import sys
+sys.path.append('../')
+from helper import *
+
+import matplotlib.pyplot as plt
+
+import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.ticker import FormatStrFormatter
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath} \usepackage{bm}']
+
+textwidth = 7.10000594991
+columnwidth = 3.35224200913
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+base_dir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
+fid_dir = base_dir + '/fid' + '/Boxes'
+cold_dir = base_dir + '/cold' + '/Boxes'
+hot_dir = base_dir + '/hot' + '/Boxes'
+dir_list = [hot_dir, fid_dir, cold_dir]
+name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
+color_list = [tb_c[1], tb_c[-1], tb_c[3]]
+
+fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
+
+for directory, name, c in zip(dir_list, name_list, color_list):
+    dTfiles = glob.glob(directory+'/delta_T*')
+    zlist = np.array([float(re.findall('z\d\d\d\.\d\d', f)[0][1:]) for f in dTfiles])
+
+    aveTb_list = []
+    for k in np.argsort(zlist):
+        Tb = np.fromfile(dTfiles[k], dtype='f4')
+        aveTb_list.append(np.mean(Tb))
+    aveTb_list = np.array(aveTb_list)
+
+    zlist = np.sort(zlist)
+
+    ax.plot(zlist, aveTb_list, label=name, c=c)
+
+ax.set_xlim(8, 14)
+ax.set_ylim(-50, 50)
+
+ax.set_xlabel(r'$z$')
+ax.set_ylabel(r'$\delta T_b\,[\,\text{mK}\,]$')
+
+ax.legend(title='model', frameon=False)
+fig.tight_layout()
+
+fig.savefig('aveTb.pdf')
+

### 2019-08-11 plots/helper.py
Update helper.py

@@ -31,10 +31,9 @@ def find_ztran(zlist, klist, xps):
         
         xps_fn_z = interp1d(zlist, this_xps)
         try:
-            sol = ridder(xps_fn_z, 9, 16)
+            sol = ridder(xps_fn_z, 9, 12.3)
         except:
             sol = np.nan
-        print(sol)
         this_ztran = float(sol)
         ztran.append(this_ztran)
 

### 2019-08-11 plots/ztran_vs_Mcut/plot_ztran_vs_Mcut.py
Make plot of ztran vs Mcut

@@ -1,0 +1,56 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+import sys
+sys.path.append('../')
+from helper import *
+
+import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.ticker import FormatStrFormatter
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath} \usepackage{bm}']
+
+textwidth = 7.10000594991
+columnwidth = 3.35224200913
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+base_dir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
+fid_dir = base_dir + '/fid' + '/MyOutput'
+cold_dir = base_dir + '/cold' + '/MyOutput'
+hot_dir = base_dir + '/hot' + '/MyOutput'
+dir_list = [hot_dir, fid_dir, cold_dir]
+name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
+color_list = [tb_c[1], tb_c[-1], tb_c[3]]
+
+Mcut_list = np.logspace(9.7, 11, 10)
+Mcut_list_label =['Mcut'+"{:2.3e}".format(Mcut) for Mcut in Mcut_list]
+
+fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
+
+for name, directory, c in zip(name_list, dir_list, color_list):
+    
+    ztran_list = []
+    for Mcut, Mcut_label in zip(Mcut_list, Mcut_list_label):
+        zlist, klist, xps = read_xps(directory+'/Halos_xps/*'+Mcut_label+'.txt')
+        klist, ztran = find_ztran(zlist, klist, xps)
+        ztran_list.append(ztran[5])
+        print(ztran[5])
+
+    ax.plot(Mcut_list, ztran_list, label=name, c=c)
+
+ax.set_xscale('log')
+
+ax.set_xlim(10.**(9.7), 1e11)
+ax.set_ylim(9.5, 14)
+
[…]

### 2019-08-11 scripts/run_halo_gen.py
Update run_halo_gen.py

@@ -10,20 +10,21 @@ basedir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
 fid_dir = basedir + '/fid'
 cold_dir = basedir + '/cold'
 hot_dir = basedir + '/hot'
-dir_list = [hot_dir, fid_dir, cold_dir]
+#dir_list = [hot_dir, fid_dir, cold_dir]
+dir_list = [fid_dir]
 
-Mcut_list = [1E9, 1E10, 1E11]
-Mcut_list_label =['Mcut1e9','Mcut1e10','Mcut1e11']
+Mcut_list = np.logspace(9.7, 11, 10)
+Mcut_list_label =['Mcut'+"{:2.3e}".format(Mcut) for Mcut in Mcut_list]
 
 for directory in dir_list:
     fin_directory = directory + '/Output_files/Halo_lists'
-    fout_directory = directory + '/MyOutput'
+    fout_directory = directory + '/MyOutput/Halo_fields'
 
-    for fin in tqdm(glob.glob(fin_directory+'/halos*')):
+    for fin in tqdm(glob.glob(fin_directory+'/updated_halos*')):
 
         z = float(re.findall('\d?\d\.\d\d', fin)[0])
         zlabel = "{:06.2f}".format(z)
 
         for Mcut,label in zip(Mcut_list,Mcut_list_label):
-            fout = fout_directory+'/halos_z'+zlabel+'_'+label
+            fout = fout_directory+'/updated_halos_z'+zlabel+'_'+label
             gen_halo_catalog(fin, fout, 256, Mcut=Mcut)

### 2019-08-12 plots/xps_vs_z/plot_xps_z.py
Update xps plot

@@ -26,15 +26,16 @@ dir_list = [hot_dir, fid_dir, cold_dir]
 name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
 color_list = [tb_c[1], tb_c[-1], tb_c[3]]
 
-Mcut_list = [1E9, 1E10, 1E11]
-Mcut_list_label =['Mcut1e9','Mcut1e10','Mcut1e11']
-ls_list = ['solid', 'dashed', 'dotted']
+#Mcut_list = [1E9, 1E10, 1E11]
+Mcut_list = [1E9]
+Mcut_list_label =['Mcut5.012e+09']
+ls_list = ['solid']
 
-fig, ax = plt.subplots(1, 1, figsize=(textwidth, columnwidth))
+fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
 
 for name, directory, c in zip(name_list, dir_list, color_list):
     for i,(label, ls) in enumerate(zip(Mcut_list_label, ls_list)):
-        zlist, klist, xps = read_xps(directory+'/halo_xps/*'+label+'*.txt')
+        zlist, klist, xps = read_xps(directory+'/Halos_xps/*'+label+'*.txt')
         klist, ztran = find_ztran(zlist, klist, xps)
         if i==0:
             ax.plot(zlist, xps[:,3], label=name, c=c, ls=ls)
@@ -44,14 +45,14 @@ for name, directory, c in zip(name_list, dir_list, color_list):
 # ax.set_xscale('log')
 ax.set_yscale('symlog')
 
-ax.set_xlim(9, 14)
+ax.set_xlim(9, 13)
 ax.set_ylim(-1e6, 1e6)
 
 ax.set_xlabel(r'$z$')
-ax.set_ylabel(r'$\Delta_{21,g}^2\,[\,\text{mK}^2\,]$')
+ax.set_ylabel(r'$\Delta_{21,g}^2\,[\,\text{mK}\,]$')
 
-ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
-ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
+# ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
+# ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
 
 ax.legend(title='model', frameon=False)
 fig.tight_layout()

### 2019-08-12 paper/ms.tex
Add def of transition redshift

@@
 
+\newcommand{\hoverMpc}{\ensuremath{h\,\text{Mpc}^{-1}}}
+
 \newcommand{\fid}{\texttt{fid}}
@@
 \newcommand{\cold}{\texttt{cold}}
+
+\newcommand{\zst}{\ensuremath{z_{\star}}}
 
@@
 \section{Methods} \label{sec:methods}
+\subsection{The transition redshift} \label{ssec:ztran_def}
+The transition redshift $\zst(k)$ is defined by a field $x$ which traces the
+density field on large scales and the condition that
+\beq \label{eq:ztran_def}
+P_{21,x}(k, \zst(k)) \equiv 0\text{.}
+\eeq
+If more than one such \zst{} exists, then we choose the lowest one where
+$P_{21,x}$ last transitioned from positive to negative.
+
 \subsection{21cmFAST} \label{ssec:tfast}

### 2019-08-12 paper/ms.tex
Add two plots to results section

@@
 
+\section{Results} \label{sec:results}
+\subsection{The halo field}
+We first investigate the dependence of the transition redshift as defined by
+the halo field. Fig.~\ref{fig:ztran_vs_k} shows the transition redshift
+defined by the 21~cm\,--\,density cross-power spectrum (see
+Eq.~\ref{eq:ztran_def}) as a function of $k$. The three models considered in
+this work are shown in orange, gray, and teal (\hot{}, \fid{}, and \cold{},
+respectively).
+
+Fig.~\ref{fig:ztran_vs_k} shows that \zst{} is only weakly a function of $k$.
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{../plots/ztran_vs_k/ztran_vs_k.pdf}
+\caption{The transition redshift ($\zst$) as defined by cross-correlating with the
+density field (solid lines) and all resolved halos (dashed lines, $M\gtrsim
+5\times10^9\,\Msun$), for our three different EoR models (\hot{}, \fid{}, and
+\cold{}). We see that \zst{} is only a mild function of $k$ for the three
+models, with slightly stronger dependence as the heating of the model
+decreases. The most dependence comes in the \cold{} model, where \zst{}
+changes by $\sim7\,\%$ from $k=0.1$ to $0.6\,\hoverMpc$. {\bf Some words for
+why cold and fid cut off at some k}}
+\label{fig:ztran_vs_k}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=\columnwidth]{../plots/ztran_vs_Mcut/ztran_vs_Mcut.pdf}
+\caption{The transition redshift (\zst) as defined by cross-correlating with the halo field for our three different EoR models (\hot{}, \fid{}, and
+\cold{}) as a function of the cut-off mass. The cross-correlation is only made
+between the 21~cm field and all halos with masses $M>M_{\text{cut}}$. One can
+see that for the \fid{} and \cold{} models, \zst{} is only mildly a function
+of $M_{\text{cut}}$ below a certain cut-off mass ($\sim10^{10.5}\,\Msun$ in
+both models). In other words, as long as a galaxy survey is deep enough so as
+to resolve a sufficient number of galaxies, the \zst{} is not dependent on the
+depth of the survey. The \hot{} model shows more dependence, but this may be
+due to sampling noise due to the smaller number of such halos at the higher
+\zst{} typical for the \hot{} model.}
+\end{figure}
+
 \section{Detectability}

### 2019-08-12 .ci/build-paper.sh
Add CI

@@ -1,0 +1,10 @@
+#!/bin/bash -x
+
+# Force push the paper to GitHub
+cd $TRAVIS_BUILD_DIR
+git checkout --orphan $TRAVIS_BRANCH-pdf
+git rm -rf .
+git add -f paper/ms.pdf
+git -c user.name='travis' -c user.email='travis' commit -m "building the paper"
+git push -q -f https://$GITHUB_USER:$GITHUB_API_KEY@github.com/$TRAVIS_REPO_SLUG $TRAVIS_BRANCH-pdf
+

### 2019-08-12 paper/ms.tex
Modify plot placements
Fix previous commit
Small updates

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[A. Beane and K. Moriwaki]{
-Angus Beane$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu}
-and Kana Moriwaki$^{2}$\thanks{E-mail: kana.moriwaki@utap.phy.s.u-tokyo.ac.jp}
+\author[A. Beane, K. Moriwaki, ...]{
+Angus Beane$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu},
+Kana Moriwaki$^{2}$,
+and others
 \\
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{../plots/ztran_vs_k/ztran_vs_k.pdf}
+\includegraphics[width=\columnwidth]{plots/ztran_vs_k.pdf}
 \caption{The transition redshift ($\zst$) as defined by cross-correlating with the
@@
 \begin{figure}
-\includegraphics[width=\columnwidth]{../plots/ztran_vs_Mcut/ztran_vs_Mcut.pdf}
+\includegraphics[width=\columnwidth]{plots/ztran_vs_Mcut.pdf}
 \caption{The transition redshift (\zst) as defined by cross-correlating with the halo field for our three different EoR models (\hot{}, \fid{}, and

### 2019-08-12 plots/ztran_vs_Mcut/plot_ztran_vs_Mcut.py
Add k print

@@ -38,7 +38,7 @@ for name, directory, c in zip(name_list, dir_list, color_list):
         zlist, klist, xps = read_xps(directory+'/Halos_xps/*'+Mcut_label+'.txt')
         klist, ztran = find_ztran(zlist, klist, xps)
         ztran_list.append(ztran[5])
-        print(ztran[5])
+        print(klist[5], ztran[5])
 
     ax.plot(Mcut_list, ztran_list, label=name, c=c)
 

### 2019-08-12 plots/aveTb/plot_aveTb.py
Update aveTb plot

@@ -28,7 +28,7 @@ dir_list = [hot_dir, fid_dir, cold_dir]
 name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
 color_list = [tb_c[1], tb_c[-1], tb_c[3]]
 
-fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
+fig, ax = plt.subplots(1, 1, figsize=(textwidth, columnwidth))
 
 for directory, name, c in zip(dir_list, name_list, color_list):
     dTfiles = glob.glob(directory+'/delta_T*')
@@ -44,8 +44,8 @@ for directory, name, c in zip(dir_list, name_list, color_list):
 
     ax.plot(zlist, aveTb_list, label=name, c=c)
 
-ax.set_xlim(8, 14)
-ax.set_ylim(-50, 50)
+ax.set_xlim(8, 25)
+ax.set_ylim(-200, 100)
 
 ax.set_xlabel(r'$z$')
 ax.set_ylabel(r'$\delta T_b\,[\,\text{mK}\,]$')

### 2019-08-12 plots/xps_vs_z/plot_xps_z.py
Update xps_vs_z plot

@@ -31,11 +31,11 @@ Mcut_list = [1E9]
 Mcut_list_label =['Mcut5.012e+09']
 ls_list = ['solid']
 
-fig, ax = plt.subplots(1, 1, figsize=(columnwidth, columnwidth))
+fig, ax = plt.subplots(1, 1, figsize=(textwidth, columnwidth))
 
 for name, directory, c in zip(name_list, dir_list, color_list):
     for i,(label, ls) in enumerate(zip(Mcut_list_label, ls_list)):
-        zlist, klist, xps = read_xps(directory+'/Halos_xps/*'+label+'*.txt')
+        zlist, klist, xps = read_xps(directory+'/xps*.txt')
         klist, ztran = find_ztran(zlist, klist, xps)
         if i==0:
             ax.plot(zlist, xps[:,3], label=name, c=c, ls=ls)
@@ -44,15 +44,16 @@ for name, directory, c in zip(name_list, dir_list, color_list):
 
 # ax.set_xscale('log')
 ax.set_yscale('symlog')
+#ax.set_xscale('log')
 
-ax.set_xlim(9, 13)
+ax.set_xlim(8, 25)
 ax.set_ylim(-1e6, 1e6)
 
 ax.set_xlabel(r'$z$')
-ax.set_ylabel(r'$\Delta_{21,g}^2\,[\,\text{mK}\,]$')
+ax.set_ylabel(r'$\Delta_{21,\delta}^2\,[\,\text{mK}\,]$')
 
-# ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
-# ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
+#ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
+#ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
 
 ax.legend(title='model', frameon=False)
 fig.tight_layout()

### 2019-08-12 plots/ztran_vs_alpha_sigma/plot_ztran_vs_alpha_sigma.py
Add ztran vs alpha/sigma plot

@@ -1,0 +1,74 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+import sys
+sys.path.append('../')
+from helper import *
+
+import matplotlib as mpl
+from matplotlib import rc
+from matplotlib.ticker import FormatStrFormatter
+rc('font', **{'family': 'serif', 'serif': ['Computer Modern']})
+rc('text', usetex=True)
+mpl.rcParams['text.latex.preamble'] = [r'\usepackage{amsmath} \usepackage{bm}']
+
+textwidth = 7.10000594991
+columnwidth = 3.35224200913
+
+tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
+        '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
+
+base_dir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
+fid_dir = base_dir + '/fid' + '/MyOutput'
+cold_dir = base_dir + '/cold' + '/MyOutput'
+hot_dir = base_dir + '/hot' + '/MyOutput'
+dir_list = [hot_dir, fid_dir, cold_dir]
+name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
+color_list = [tb_c[1], tb_c[-1], tb_c[3]]
+
+alpha_fid = 1
+sigma_fid = 0.4
+alpha_fid_label = 'alpha'+"{:.3f}".format(alpha_fid)
+sigma_fid_label = 'sigma'+"{:.3f}".format(sigma_fid)
+
+alpha_list = np.linspace(0.5, 1.5, 11)
+sigma_list = np.linspace(0.0, 0.8, 11)
+alpha_label_list = ['alpha'+"{:.3f}".format(alpha) for alpha in alpha_list]
+sigma_label_list = ['sigma'+"{:.3f}".format(sigma) for sigma in sigma_list]
+
+fig, ax = plt.subplots(1, 2, figsize=(textwidth, columnwidth), sharey=True)
+
+for name, directory, c in zip(name_list, dir_list, color_list):
+    
+    ztran_list = []
+    for alpha_label in alpha_label_list:
+        print(directory+'/IM_xps/*'+alpha_label+'_'+sigma_fid_label)
[…]

### 2019-08-12 paper/ms.tex
Update section on luminosity model

@@
 
-\subsection{[\OIII] luminosity} \label{ssec:oiii_lum}
-
+\subsection{[\OIII] intensity mapping} \label{ssec:oiii_int_map}
 In order to model the relation between [\OIII] luminosity ($L_{\OIII}$) and
 halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
-the luminosity for halo $j$
+the mean luminosity of a halo of mass $M$ is,
 \beq \label{eq:lum_mass_relation}
-L_j(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha} + s_j(w)
+\avg{L}(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha}\text{,}
 \eeq
 where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
-[\OIII] at that redshift, $\alpha$ is the power-law index, and $s_j(w)$ is a
-number randomly selected from a lognormal distribution with zero mean and
-width $w$. Once the average intensity is fixed (which we assume so), this is a
-two-parameter model ($\alpha$ and $w$) of the [\OIII] luminosity-mass
-relation.
+[\OIII] at that redshift and $\alpha$ is the power-law index. We then draw the
+luminosity of each halo from a lognormal distribution of mean $\avg{L}(M)$ and
+scatter $\sigma$. Once the average intensity is fixed (which we assume so),
+this is a two-parameter model ($\alpha$ and $\sigma$) of the [\OIII]
+luminosity-mass relation. In practice, the average intensity of the field only
+enters in the detectability calculation, so we instead work in the convenient
+units where $L_0=1$ and $M_0=10^{10}\,\Msun$.
 

### 2019-08-12 plots/ztran_vs_alpha_sigma/plot_ztran_vs_alpha_sigma.py
Get numerical values for zstar variations

@@ -42,12 +42,13 @@ for name, directory, c in zip(name_list, dir_list, color_list):
     
     ztran_list = []
     for alpha_label in alpha_label_list:
-        print(directory+'/IM_xps/*'+alpha_label+'_'+sigma_fid_label)
+        # print(directory+'/IM_xps/*'+alpha_label+'_'+sigma_fid_label)
         zlist, klist, xps = read_xps(directory+'/IM_xps/*'+alpha_label+'_'+sigma_fid_label)
         klist, ztran = find_ztran(zlist, klist, xps)
         ztran_list.append(ztran[5])
-        print(klist[5], ztran[5])
+        # print(klist[5], ztran[5])
 
+    print(name, 'alpha variation:', 100.0*(np.max(ztran_list) - np.min(ztran_list))/np.mean(ztran_list))
     ax[0].plot(alpha_list, ztran_list, label=name, c=c)
 
     ztran_list = []
@@ -55,8 +56,9 @@ for name, directory, c in zip(name_list, dir_list, color_list):
         zlist, klist, xps = read_xps(directory+'/IM_xps/*'+alpha_fid_label+'_'+sigma_label)
         klist, ztran = find_ztran(zlist, klist, xps)
         ztran_list.append(ztran[5])
-        print(klist[5], ztran[5])
+        # print(klist[5], ztran[5])
 
+    print(name, 'sigma variation:', 100.0*(np.max(ztran_list) - np.min(ztran_list))/np.mean(ztran_list))
     ax[1].plot(sigma_list, ztran_list, c=c)
 
 

### 2019-08-12 paper/ms.tex
Add bit about generating the halo field

@@
 
-\subsection{[\OIII] intensity mapping} \label{ssec:oiii_int_map}
-In order to model the relation between [\OIII] luminosity ($L_{\OIII}$) and
+We generate the halo field using the included halo finder in \tfast{}. This
+halo finder is a remnant of an earlier version of the code
+\citep{2007ApJ...669..663M} and is typically unused in standard
+configurations. It is based upon the ``peak-patch'' algorithm for halo finding
+introduced by \citet{1996ApJS..103....1B}.
+
+\subsection{Intensity mapping} \label{ssec:oiii_int_map}
+In order to model the relation between luminosity ($L$) and
 halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that

### 2019-08-12 paper/ms.tex
Add more about intensity mapping, remove [OIII] references

@@
 where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
-[\OIII] at that redshift and $\alpha$ is the power-law index. We then draw the
+the line at that redshift and $\alpha$ is the power-law index. We then draw the
 luminosity of each halo from a lognormal distribution of mean $\avg{L}(M)$ and
 scatter $\sigma$. Once the average intensity is fixed (which we assume so),
-this is a two-parameter model ($\alpha$ and $\sigma$) of the [\OIII]
+this is a two-parameter model ($\alpha$ and $\sigma$) of the
 luminosity-mass relation. In practice, the average intensity of the field only
@@
 
+We assign a luminosity to each halo according to this prescription. An
+important consideration is that we have not specified which line we are
+working with. In detail, the relationship between a halo and it's luminosity
+is a complicated function of the state of the interstellar medium of the
+hosted galaxy, which can depend upon a number of both deterministic and
+stochastic quantities. Our model crudely attempts to account for this by
+including some random scatter, but will ultimately be a rough description of
+reality.
+
+{\bf Some words justifying why our simple model will extend to more
+complicated luminosity-halo relations.}
+
 \section{Results} \label{sec:results}
 \subsection{The halo field}
+{\bf If we switch to LIM I think this section should be scrapped, except
+showing ztran vs k but using LIM and density instead of halos}
+
 We first investigate the dependence of the transition redshift as defined by

### 2019-08-12 paper/ms.tex
Add really exciting figure!!

@@
 
+\subsection{Line-intensity mapping} \label{ssec:lim}
+We now turn to understanding how \zst{} depends on the parameters of our
+generic line-intensity mapping field: the slope ($\alpha$) and lognormal
+scatter ($\sigma$). See \S~\ref{ssec:oiii_int_map} for more details of the
+construction of the field.
+
+In Fig.~\ref{fig:ztran_vs_alpha_sigma} we plot \zst{} as a function of each of
+these parameters\,--\,$\alpha$ and $\sigma$. We see that \zst{} is remarkably
+insensitive to the value of either of these parameters, with some small
+deviation as a function of $\alpha$. The \hot{}, \fid{}, and \cold{} models
+only vary by a total of $1.2\%$, $0.56\%$, $0.52\%$ with respect to $\alpha$,
+and $0.070\%$, $0.10\%$, and $0.11\%$ with respect to $\sigma$, respectively.
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{plots/ztran_vs_alpha_sigma.pdf}
+\caption{The transition redshift (\zst) defined by cross-correlating with a
+generic two-parameter intensity mapping field. The parameter $\alpha$ sets the
+slope of the luminosity-mass relation and the parameter $\sigma$ sets the
+lognormal scatter in this relation (see \S~\ref{ssec:oiii_int_map}). The
+\hot{}, \fid{}, and \cold{} models only vary by a total of $1.2\%$, $0.56\%$,
+$0.52\%$ with respect to $\alpha$, and $0.070\%$, $0.10\%$, and $0.11\%$ with
+respect to $\sigma$, respectively. Clearly \zst{} varies only with the
+structure of the 21~cm field, and is thus an excellent probe of reionization.}
+\label{fig:ztran_vs_alpha_sigma}
+\end{figure*}
+
 \section{Detectability}

### 2019-08-12 paper/ms.tex
Add beginning of detectability section

@@
 \section{Detectability}
+Up to this point, we have not been specific about which galactic emission line
+one might consider using to measure \zst{}. This is because computing \zst{}
+from our simulations with our simple line intensity model
+(\S~\ref{ssec:oiii_int_map}) does not require specifying the total average
+intensity of the field.
+
+The variance of the cross-spectrum between the 21~cm field and a line $i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}
+\beq \label{eq:var_xps}
+\text{Var}\left[P_{21,i}\right] = P_{21,i}^2 + P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
+\eeq
+where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
+noise contribution, and is similarly defined for $P_{i,\text{tot}}$.
 

### 2019-08-13 plots/aveTb/plot_aveTb.py
Update aveTb plot, add nf

@@ -21,37 +21,61 @@ tb_c = ['#4e79a7', '#f28e2b', '#e15759', '#76b7b2', '#59a14f',
         '#edc948', '#b07aa1', '#ff9da7', '#9c755f', '#bab0ac']
 
 base_dir = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256'
-fid_dir = base_dir + '/fid' + '/Boxes'
-cold_dir = base_dir + '/cold' + '/Boxes'
-hot_dir = base_dir + '/hot' + '/Boxes'
+fid_dir = base_dir + '/fid'
+cold_dir = base_dir + '/cold'
+hot_dir = base_dir + '/hot'
 dir_list = [hot_dir, fid_dir, cold_dir]
 name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
+fname_list = ['hot', 'fid', 'cold']
 color_list = [tb_c[1], tb_c[-1], tb_c[3]]
 
-fig, ax = plt.subplots(1, 1, figsize=(textwidth, columnwidth))
+fig, ax = plt.subplots(2, 1, figsize=(textwidth, 1.2*columnwidth), sharex=True)
 
-for directory, name, c in zip(dir_list, name_list, color_list):
-    dTfiles = glob.glob(directory+'/delta_T*')
-    zlist = np.array([float(re.findall('z\d\d\d\.\d\d', f)[0][1:]) for f in dTfiles])
+for directory, name, fname, c in zip(dir_list, name_list, fname_list, color_list):
+    try:
+        zlist = np.load('zlist_'+fname+'.npy')
+        nflist = np.load('nflist_'+fname+'.npy')
+        aveTb_list = np.load('Tblist_'+fname+'.npy')
+        ztran = np.load('ztran_'+fname+'.npy')
+    except:
+        dTfiles = glob.glob(directory+'/Boxes/delta_T*')
+        zlist = np.array([float(re.findall('z\d\d\d\.\d\d', f)[0][1:]) for f in dTfiles])
+        nflist = np.array([float(re.findall('nf\d.\d\d\d\d\d\d', f)[0][2:]) for f in dTfiles])
 
-    aveTb_list = []
-    for k in np.argsort(zlist):
-        Tb = np.fromfile(dTfiles[k], dtype='f4')
-        aveTb_list.append(np.mean(Tb))
[…]

### 2019-08-13 plots/aveTb/plot_aveTb.py
Add xps row to aveTb plot

@@ -29,7 +29,7 @@ name_list = [r'\texttt{hot}', r'\texttt{fid}', r'\texttt{cold}']
 fname_list = ['hot', 'fid', 'cold']
 color_list = [tb_c[1], tb_c[-1], tb_c[3]]
 
-fig, ax = plt.subplots(2, 1, figsize=(textwidth, 1.2*columnwidth), sharex=True)
+fig, ax = plt.subplots(3, 1, figsize=(textwidth, 1.5*1.2*columnwidth), sharex=True)
 
 for directory, name, fname, c in zip(dir_list, name_list, fname_list, color_list):
     try:
@@ -37,6 +37,7 @@ for directory, name, fname, c in zip(dir_list, name_list, fname_list, color_list
         nflist = np.load('nflist_'+fname+'.npy')
         aveTb_list = np.load('Tblist_'+fname+'.npy')
         ztran = np.load('ztran_'+fname+'.npy')
+        xps_to_plot = np.load('xps_to_plot_'+fname+'.npy')
     except:
         dTfiles = glob.glob(directory+'/Boxes/delta_T*')
         zlist = np.array([float(re.findall('z\d\d\d\.\d\d', f)[0][1:]) for f in dTfiles])
@@ -51,6 +52,8 @@ for directory, name, fname, c in zip(dir_list, name_list, fname_list, color_list
         this_zlist, klist, xps = read_xps(directory+'/MyOutput/xps*')
         klist, ztran = find_ztran(this_zlist, klist, xps)
         # ztran = ztran[5]
+        xps_to_plot = klist[3]**3 * xps[:,3]/(2.*np.pi**2)
+        print('k=', klist[3])
     
         keys = np.argsort(zlist)
         nflist = nflist[keys]
@@ -60,19 +63,26 @@ for directory, name, fname, c in zip(dir_list, name_list, fname_list, color_list
         np.save('nflist_'+fname+'.npy', nflist)
         np.save('Tblist_'+fname+'.npy', aveTb_list)
         np.save('ztran_'+fname+'.npy', ztran)
+        np.save('xps_to_plot_'+fname+'.npy', xps_to_plot)
 
     ax[0].plot(zlist, 1.-nflist, c=c, label=name)
[…]

### 2019-08-13 paper/ms.tex
Line indent fix
Add some more commands
Add aveTb plot to paper

@@
 \newcommand{\OIII}{\ensuremath{\text{O~\textsc{iii}}}}
+\newcommand{\NII}{\ensuremath{\text{N~\textsc{ii}}}}
+
+\newcommand{\Ha}{\ensuremath{\text{H}\alpha}}
+\newcommand{\Hb}{\ensuremath{\text{H}\beta}}
 
@@
 \newcommand{\kms}{\ensuremath{\text{km}\,\text{s}^{-1}}}
+\newcommand{\SFR}{\ensuremath{\text{SFR}}}
+\newcommand{\yr}{\ensuremath{\text{yr}}}
 
@@
 \newcommand{\zst}{\ensuremath{z_{\star}}}
+\newcommand{\E}[1]{\mathrm{E}[#1]}
+\newcommand{\Var}[1]{\mathrm{Var}[#1]}
+\newcommand{\Cov}[2]{\mathrm{Cov}[#1,#2]}
 
@@
 \section{Results} \label{sec:results}
+\subsection{The transition redshift} \label{ssec:ztran_results}
+
+\begin{figure*}
+\includegraphics[width=\textwidth]{plots/aveTb_nf.pdf}
+\caption{A summary of the ionization and heating history of our three EoR
+models: \hot{}, \fid{}, and \cold{}. \textit{Upper}: the ionization history of
+each model, showing that reionization begins ($\avg{x_{\HII}}\sim0.01$) at
+$z\sim16$ and ends at $z\sim6$ in each model. In detail the ionization
+histories are slightly different, but not drastically. \textit{Lower}: the
+heating history of each model, showing the strong differences in the monopole
+signal. The transition redshift \zst{} (defined where $P_{21,\delta}(\zst{}) =
+0$) for each model is shown as a vertically dashed line. We see that models in
+which heating is more efficient have an earlier \zst{}.}
+\label{fig:aveTb_nf}
+\end{figure*}
+
 \subsection{The halo field}
@@
 \includegraphics[width=\columnwidth]{plots/ztran_vs_Mcut.pdf}
-\caption{The transition redshift (\zst) as defined by cross-correlating with the halo field for our three different EoR models (\hot{}, \fid{}, and
+\caption{The transition redshift (\zst) as defined by cross-correlating with
+the halo field for our three different EoR models (\hot{}, \fid{}, and
 \cold{}) as a function of the cut-off mass. The cross-correlation is only made

### 2019-08-13 paper/ms.tex
Expand detectability section to talk about CDIM

@@
 Up to this point, we have not been specific about which galactic emission line
-one might consider using to measure \zst{}. This is because computing \zst{}
-from our simulations with our simple line intensity model
-(\S~\ref{ssec:oiii_int_map}) does not require specifying the total average
-intensity of the field.
+one might consider using to measure \zst{}\,--\,in fact, our entire formalism
+could be executed using a galaxy survey, if one with sufficient redshift
+accuracy and depth could be executed. While it will not be possible for a
+traditional galaxy survey to extend to $z\sim10$ in the near future, it may be
+possible to execute a survey of line-emitting galaxies, e.g., with
+[\OIII]-emitters \citep{2018MNRAS.481L..84M, 2019arXiv190610863M}.
+
+In this work we will consider the prospect of performing intensity mapping
+measurements of the H$\alpha$ line using the proposed, space-based Cosmic Dawn
+Intensity Mapper (CDIM) \citep{2019arXiv190303144C}. CDIM is an infrared
+telescope with an $83\,\text{cm}$ dish capable of measuring $R=300$ spectra
+from wavelengths $0.75\,\mu\text{m}$ to $7.5\,\mu\text{m}$. Therefore, CDIM
+will be able to measure the H-$\alpha$ line ($656\,\text{nm}$) from $z=0.14$
+to $10.4$ and the H-$\beta$ line ($486\,\text{nm}$) from $z=0.54$ to $14.4$,
+so long as there is a detectable signal. We choose to study the H-$\alpha$ and
+H-$\beta$ lines since the uncertainty regarding their total intensity at
+$z\sim10$ should be less uncertain than for lines that require metal
+enrichment such as [\CII], [\OIII], or [\NII], since the total metal
+enrichment of the universe is quickly declining at these high $z$
 

### 2019-08-13 paper/ms.tex
Add how avg Halpha I is computed

@@
 
+We assume a linear relationship between H-$\alpha$ luminosity and star
+formation rate \citep{1998ARA&A..36..189K}:
+\beq \label{eq:LHalpha_SFR}
+\begin{split}
+L_{\Ha} &= 3.29\times10^{7} \left(\frac{\SFR}{1\,\Msun\,\yr^{-1}}\right) L_{\odot} \\
+        &\equiv L_{0,\Ha} \left(\frac{\SFR}{1\,\Msun\,\yr^{-1}}\right)
+\end{split}
+\eeq
+This relation is based on a Salpeter IMF and is calibrated towards local
+galaxies. As discussed in \citet{2019MNRAS.487.5902K}, the reality of
+$z\sim10$ galaxies may be slightly different\,--\,the IMF may be more top
+heavy, and the metal-poor nature of a typical star will naturally produce more
+ionizing photons. However, the escape of ionizing photons may be more
+efficient at higher redshift, and the conventional relation assumes no escape.
+\citet{2019MNRAS.487.5902K} provide a slightly shallower fitting form for the
+$L_{\Ha}-\SFR$ relation based upon their simulations, but we choose to use the
+conventional relation here.
+
+We use a fitting formula for the SFRd calibrated upon galaxies from $z=0$ to
+$8$ \citep{2014ARA&A..52..415M}
+\beq \label{eq:sfrd}
+\psi(z) = 0.015 \frac{(1+z)^{2.7}}{1+\left[(1+z)/2.9\right]^{5.6}}\,M_{\odot}\yr^{-1}\Mpc^{-3} \text{.}
+\eeq
+The comoving emissitivity of the \Ha{} line can then be readily computed as,
+\beq \label{eq:Ha_emiss}
+\epsilon_{\Ha}(z) = L_{0,\Ha} \psi(z)\text{.}
+\eeq
+The average specific intensity can be computed from the comoving emissitivity
+as \citep{2011ApJ...741...70L,2013ApJ...768...15P},
+\beq \label{eq:int_from_em}
+\avg{I_{\Ha}}(z) = \frac{\epsilon_{\Ha}(z)}{4\pi\nu_{\text{rest},\Ha}} \frac{c}{H(z)}
+\eeq
+
 The variance of the cross-spectrum between the 21~cm field and a line $i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}

### 2019-08-13 paper/ms.tex
Touch up detectability section

@@
 
-The variance of the cross-spectrum between the 21~cm field and a line $i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}
+The variance of the cross-spectrum between the 21~cm field and a line $i$ is
+given by \citep[e.g.][]{2007ApJ...660.1030F}
 \beq \label{eq:var_xps}
-\text{Var}\left[P_{21,i}\right] = P_{21,i}^2 + P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
+\Var{P_{21,i}} = P_{21,i}^2 + 
+                                  P_{21,\text{tot}} P_{i,\text{tot}}\text{,}
 \eeq
 where $P_{21,\text{tot}} = P_{21,21} + N_{21}$, where $N_{21}$ is the total
-noise contribution, and is similarly defined for $P_{i,\text{tot}}$.
+noise contribution. $P_{i,\text{tot}}$ is defined similarly.
+
+By expanding $P_{21,i}$ as a linear function about \zst{}, we can estimate the
+error on \zst{} by
+\beq \label{eq:error_on_zst}
+\Var{\zst} = \left(\left.\frac{\partial P_{21,i}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,i}}
+\eeq
 

### 2019-08-13 plots/helper.py
Add Halpha intensity to helper.py

@@ -4,6 +4,14 @@ import re
 from scipy.interpolate import interp1d
 from scipy.optimize import ridder
 
+import astropy.units as u
+from astropy.constants import c
+
+from colossus.cosmology import cosmology
+
+params = {'flat': True, 'H0': 67.66, 'Om0': 0.3111, 'Ob0': 0.02242/(0.6766**2), 'sigma8': 0.8102, 'ns': 0.9665}
+cosmo = cosmology.setCosmology('myCosmo', params)
+
 h = 0.6766
 
 def read_xps(files):
@@ -92,3 +100,19 @@ def compute_power_spectrum(field, Lbox, npix, kmin=None, kmax=None, deltak=1.4):
     Pklist = np.histogram(kmag_1d, bins, weights=np.square(np.absolute(field_ft_1d))/volume)[0]/Nlist
 
     return klist, Pklist
+
+def Halpha_intensity(z):
+    def psi(zp):
+        ans = 0.015
+        ans *= (1+zp)**(2.7)
+        ans /= 1 + ((1+zp)/2.9)**(5.6)
+        return ans
+
+    psi_at_z = psi(z) * u.Msun/u.year/(u.Mpc**3)
+    L0 = 3.29E7 * u.Lsun / (u.Msun/u.year)
+    Hz = cosmo.Hz(z) * u.km/u.s/u.Mpc
+    nurest_Ha = c/(656.28 * u.nm)
+
+    ans = (L0*psi_at_z / (4.*np.pi*nurest_Ha)) * (c/Hz)
+    return ans
+

### 2019-08-14 paper/ms.tex
Add info about survey overlap w 21cm
Add more stuff to detectability

@@
 to $10.4$ and the H-$\beta$ line ($486\,\text{nm}$) from $z=0.54$ to $14.4$,
-so long as there is a detectable signal. We choose to study the H-$\alpha$ and
-H-$\beta$ lines since the uncertainty regarding their total intensity at
-$z\sim10$ should be less uncertain than for lines that require metal
-enrichment such as [\CII], [\OIII], or [\NII], since the total metal
-enrichment of the universe is quickly declining at these high $z$
+so long as there is a detectable signal. CDIM will execute a wide, medium, and
+deep survey of $311$, $31.1$, and $15.6\,\text{deg}^2$, respectively. However,
+only the medium survey's field will overlap with 21~cm experiments (HERA and a
+deep field from SKA1-LOW). Therefore we will only consider the medium survey.
+
+We choose to study the H-$\alpha$ and H-$\beta$ lines since the uncertainty
+regarding their total intensity at $z\sim10$ should be less uncertain than for
+lines that require metal enrichment such as [\CII], [\OIII], or [\NII], since
+the total metal enrichment of the universe is quickly declining at these high
+$z$
 
@@
 
-The variance of the cross-spectrum between the 21~cm field and a line $i$ is
-given by \citep[e.g.][]{2007ApJ...660.1030F}
+The variance per mode of the cross-spectrum between the 21~cm field and a line
+$i$ is given by \citep[e.g.][]{2007ApJ...660.1030F}
 \beq \label{eq:var_xps}
@@
 
+In detail $N_{\Ha}$ will have a frequency-dependent structure, but for
+$z\sim9$ to $10$, it is reasonable to assume a conservative, constant value of
+$N_{\Ha}\sim4\times10^4\,\text{Jy}/\text{sr}$ for the medium survey. For
+$N_{21}$, we assume that $N_{21} = P_{21,21}(k=0.1\,\text{Mpc}^{-1})$, a
+reasonable approximation given that HERA-350 will image some large scale modes
+\citep{2017PASP..129d5001D}, as discussed previously \citep{2018ApJ...867...26B}.
+
+The number of modes is given by,
+\beq \label{eq:nmodes}
+N_m = \frac{4\pi k^2 \delta k}{V_{\text{fund}}}\text{,}
+\eeq
+where $\delta k$ is the width of the $k$-bin and $V_{\text{fund}}$ is the
+volume of a fundamental mode. We assume a square survey area, and so this is
+given by,
+\beq \label{eq:fund}
+V_{\text{fund}} = \frac{(2 \pi)^3}{L_{\perp}^2 L_{\parallel}}\text{,}
+\eeq
+where $L_{\perp}$ is the  and $L_{\parallel}$ is the comoving
+length of the redshift extent of the bin. The optimal redshift binning is not
+entirely clear, since the observational target is not the power spectrum. We
+assume a redshift bin of $\Delta z = 0.03$, which is smaller than the expected
+error we compute on \zst{}, and so is not an unreasonable choice.
+
+We assume a $k$-bin of fairly large width, from $k=0.1$ to $0.3\,\Mpc^{-1}$.
+
 By expanding $P_{21,i}$ as a linear function about \zst{}, we can estimate the
@@
 \eeq
-
-\section{To cite}
-Papers that need to be cited:
-
-The Cross-Correlation of High-Redshift 21 cm and Galaxy Surveys
-\url{https://arxiv.org/abs/astro-ph/0611274}
-
-Probing Reionization with the 21 cm-Galaxy Cross Power Spectrum
-\url{https://arxiv.org/abs/0806.1055}
-
-The HI Bias during the Epoch of Reionization, discusses the positive/negative
-correlation transition as a function of $k$
-\url{https://arxiv.org/abs/1907.05098}
 

### 2019-08-14 plots/helper.py
Update read_xps to also return auto ps

@@ -14,23 +14,34 @@ cosmo = cosmology.setCosmology('myCosmo', params)
 
 h = 0.6766
 
-def read_xps(files):
+def read_xps(files, return_auto=False):
     xps_list = glob.glob(files)
     zlist = np.array([float(re.findall('\d\d\d\.\d\d', f)[0]) for f in xps_list])
     
     output = []
+    output_auto1 = []
+    output_auto2 = []
     for i,key in enumerate(np.argsort(zlist)):
         fname = xps_list[key]
         data = np.genfromtxt(fname)
         xps = data[:,3]
+        auto1 = data[:,1]
+        auto2 = data[:,2]
         output.append(xps)
+        output_auto1.append(auto1)
+        output_auto2.append(auto2)
         if i ==0:
             klist = data[:,0]/h
     
     zlist = np.sort(zlist)
 
     output = np.array(output)
-    return zlist, klist, output
+    output_auto1 = np.array(output_auto1)
+    output_auto2 = np.array(output_auto2)
+    if return_auto:
+        return zlist, klist, output, output_auto1, output_auto2
+    else:
+        return zlist, klist, output
 
 def find_ztran(zlist, klist, xps):
     ztran = []

### 2019-08-14 plots/helper.py
Return Halpha intenstiy in Jy/sr

@@ -125,5 +125,5 @@ def Halpha_intensity(z):
     nurest_Ha = c/(656.28 * u.nm)
 
     ans = (L0*psi_at_z / (4.*np.pi*nurest_Ha)) * (c/Hz)
-    return ans
+    return ans.to_value(u.Jy)
 

### 2019-08-14 plots/helper.py
Add calc_vpix.py

@@ -127,3 +127,21 @@ def Halpha_intensity(z):
     ans = (L0*psi_at_z / (4.*np.pi*nurest_Ha)) * (c/Hz)
     return ans.to_value(u.Jy)
 
+def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
+    dlambda = wave_obs/R
+    wave_upper = wave_obs + dlambda/2.0
+    wave_lower = wave_obs - dlambda/2.0
+
+    z_upper = (wave_upper-wave_emit)/wave_emit
+    z_lower = (wave_lower-wave_emit)/wave_emit
+
+    d_upper = cosmo.comovingDistance(z_max=z_upper)
+    d_lower = cosmo.comovingDistance(z_max=z_lower)
+    volume = (4.*np.pi/3.) * (d_upper**3 - d_lower**3)
+
+    Apix = (pix_length_in_arcsecond * u.arcsecond)**2
+    Apix = Apix.to_value(u.deg**2)
+    Apix_fraction = Apix/41253
+
+    return Apix_fraction * volume
+

### 2019-08-14 plots/helper.py
Add Nmodes calculator

@@ -145,3 +145,16 @@ def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
 
     return Apix_fraction * volume
 
+def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
+    z_upper = z + deltaz/2.0
+    z_lower = z - deltaz/2.0
+    dlos = cosmo.comovingDistance(z_lower, z_upper)
+
+    # convert A surv to on sky width
+    Lindeg = np.sqrt(Asurv)
+    Lperp = cosmo.angularDiameterDistance(z) * Lindeg * (np.pi/180.)
+
+    Vfund = (2.*np.pi)**3 / (Lperp**2 * dlos)
+
+    return 4.*np.pi*k**2 * deltak / Vfund
+

### 2019-08-14 plots/helper.py
Add SNR calc given some parameters

@@ -158,3 +158,22 @@ def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
 
     return 4.*np.pi*k**2 * deltak / Vfund
 
+def _calc_snr_(zst, P21, Pdelta, P21delta_deriv, N21, Nmodes, b, I, sigma=4E4, wave_emit=0.65628):
+    wave_obs = (1.+zst)*wave_emit
+    Vpix = calc_vpix(wave_obs)
+    NHa = sigma**2 * Vpix
+
+    Pi = b**2 * I**2 * Pdelta
+    xps = np.sqrt(Pi*P21)
+
+    P21tot = P21 + N21
+    Pitot = Pi + NHa
+
+
+    varP21i = xps**2 + P21tot*Pitot
+
+    P21i_deriv = b * I * P21delta_deriv
+
+    varz = varP21i / (P21i_deriv**2)
+    return np.sqrt(varz/Nmodes)
+

### 2019-08-14 plots/helper.py
Add wrapper over snr function

@@ -6,6 +6,7 @@ from scipy.optimize import ridder
 
 import astropy.units as u
 from astropy.constants import c
+from scipy.interpolate import interp2d
 
 from colossus.cosmology import cosmology
 
@@ -176,4 +177,31 @@ def _calc_snr_(zst, P21, Pdelta, P21delta_deriv, N21, Nmodes, b, I, sigma=4E4, w
 
     varz = varP21i / (P21i_deriv**2)
     return np.sqrt(varz/Nmodes)
+
+def snr_wrapper(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, deltaz, b=4):
+    keval = (kmin+kmax)/2.0
+    deltak = kmax - kmin
+
+    fn = interp2d(zlist, klist, np.transpose(xps))
+    fn_pdelta = interp2d(zlist, klist, np.transpose(pdelta))
+    fn_p21 = interp2d(zlist, klist, np.transpose(p21))
+
+    I = Halpha_intensity(zst)
+
+    # i know im numerically differentiating an interpolation
+    # i know im a bad person, pls do not write me angry emails about it
+    # or do it might be kind of entertaining
+    Pup = fn(zst+0.01, keval)
+    Pdown = fn(zst-0.01, keval)
+    Pderiv = (Pup-Pdown)/0.02
+
+    P21 = fn_p21(zst, keval)
+    Pdelta = fn_pdelta(zst, keval)
+    N21 = fn_p21(zst, 0.1)
+
+    Nm = Nmodes(keval, deltak, zst, deltaz)
+    print(Nm)
+
+    sigmazst = _calc_snr_(zst, P21, Pdelta, Pderiv, N21, Nm, b, I)
+    return float(sigmazst)
 

### 2019-08-14 plots/helper.py
Add snr in quadrature

@@ -205,3 +205,15 @@ def snr_wrapper(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, deltaz, b=4):
     sigmazst = _calc_snr_(zst, P21, Pdelta, Pderiv, N21, Nm, b, I)
     return float(sigmazst)
 
+def add_snr_in_quadrature(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, Nk, deltaz, b=4):
+    kbins = np.linspace(kmin, kmax, Nk)
+    sigmaz_tot = 0
+    for i in range(len(kbins)-1):
+        this_kmin = kbins[i]
+        this_kmax = kbins[i+1]
+        this_sigmaz = snr_wrapper(zst, zlist, klist, xps, pdelta, p21, this_kmin, this_kmax, deltaz, b=4)
+        sigmaz_tot += this_sigmaz**(-2) # add them in inverse quadrature
+    sigmaz_tot = sigmaz_tot**(-0.5)
+    return sigmaz_tot
+
+

### 2019-08-14 plots/helper.py
Some testing

@@ -217,3 +217,8 @@ def add_snr_in_quadrature(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, Nk, d
     return sigmaz_tot
 
 
+if __name__ == '__main__':
+    directory = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256/fid/MyOutput'
+    zlist, klist, xps, pdelta, p21 = read_xps(directory+'/xps*', return_auto=True)
+
+    sigmazst = add_snr_in_quadrature(10, zlist, klist, xps, pdelta, p21, 0.1, 1.0, 10, 0.1)

### 2019-08-14 paper/ms.tex
Update about surface brightness calc

@@
 
-In detail $N_{\Ha}$ will have a frequency-dependent structure, but for
-$z\sim9$ to $10$, it is reasonable to assume a conservative, constant value of
-$N_{\Ha}\sim4\times10^4\,\text{Jy}/\text{sr}$ for the medium survey. For
+In detail the surface brightness sensitivity will have a frequency-dependent
+structure, but for $z\sim9$ to $10$, it is reasonable to assume a
+conservative, constant value of
+$\sigma_{\Ha}\sim4\times10^4\,\text{Jy}/\text{sr}$ for the medium survey. To
+convert the surface brightness sensitivity to a power spectrum noise, we simply
+write,
+\beq \label{eq:ps_}
+N_{\Ha} = \sigma_{\Ha}^2 V_{\text{voxel}}\text{,}
+\eeq 
+where $V_{\text{voxel}}$ is the comoving volume of one voxel. To compute this
+we use the fact that CDIM will have $1''$ pixels and a resolution of $R=300$.
+
+For
 $N_{21}$, we assume that $N_{21} = P_{21,21}(k=0.1\,\text{Mpc}^{-1})$, a

### 2019-08-14 paper/ms.tex
Update ms.tex

@@
 \eeq
-where $L_{\perp}$ is the  and $L_{\parallel}$ is the comoving
-length of the redshift extent of the bin. The optimal redshift binning is not
-entirely clear, since the observational target is not the power spectrum. We
-assume a redshift bin of $\Delta z = 0.03$, which is smaller than the expected
-error we compute on \zst{}, and so is not an unreasonable choice.
+where $L_{\perp}$ is the  and $L_{\parallel}$ is the comoving length of the
+redshift extent of the bin. The optimal redshift binning is not entirely
+clear, since the observational target is not the power spectrum. We assume a
+redshift bin of $\Delta z = 0.03$, which is smaller than the expected error we
+compute on \zst{}, and so is not an unreasonable choice. We assume a $k$-bin
+of fairly large width, from $k=0.1$ to $0.4\,\Mpc^{-1}$.
 
-We assume a $k$-bin of fairly large width, from $k=0.1$ to $0.3\,\Mpc^{-1}$.
-
-By expanding $P_{21,i}$ as a linear function about \zst{}, we can estimate the
+By expanding $P_{21,\Ha}$ as a linear function about \zst{}, we can estimate the
 error on \zst{} by
 \beq \label{eq:error_on_zst}
-\Var{\zst} = \left(\left.\frac{\partial P_{21,i}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,i}}
+\Var{\zst} = \left(\left.\frac{\partial P_{21,\Ha}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,\Ha}}\text{,}
 \eeq
+where ${\partial P_{21,\Ha}}/{\partial z}$ is computed numerically.
 

### 2019-08-15 plots/helper.py
Fix little h issues

@@ -32,7 +32,7 @@ def read_xps(files, return_auto=False):
         output_auto1.append(auto1)
         output_auto2.append(auto2)
         if i ==0:
-            klist = data[:,0]/h
+            klist = data[:,0]
     
     zlist = np.sort(zlist)
 
@@ -136,8 +136,8 @@ def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
     z_upper = (wave_upper-wave_emit)/wave_emit
     z_lower = (wave_lower-wave_emit)/wave_emit
 
-    d_upper = cosmo.comovingDistance(z_max=z_upper)
-    d_lower = cosmo.comovingDistance(z_max=z_lower)
+    d_upper = cosmo.comovingDistance(z_max=z_upper)/cosmo.h
+    d_lower = cosmo.comovingDistance(z_max=z_lower)/cosmo.h
     volume = (4.*np.pi/3.) * (d_upper**3 - d_lower**3)
 
     Apix = (pix_length_in_arcsecond * u.arcsecond)**2
@@ -149,11 +149,11 @@ def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
 def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
     z_upper = z + deltaz/2.0
     z_lower = z - deltaz/2.0
-    dlos = cosmo.comovingDistance(z_lower, z_upper)
+    dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
 
     # convert A surv to on sky width
     Lindeg = np.sqrt(Asurv)
-    Lperp = cosmo.angularDiameterDistance(z) * Lindeg * (np.pi/180.)
+    Lperp = cosmo.angularDiameterDistance(z)/cosmo.h * Lindeg * (np.pi/180.)
 
     Vfund = (2.*np.pi)**3 / (Lperp**2 * dlos)
 

### 2019-08-15 plots/helper.py
Add ability to get varp21 from functions

@@ -150,6 +150,7 @@ def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
     z_upper = z + deltaz/2.0
     z_lower = z - deltaz/2.0
     dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
+    print(z, deltaz, z_lower, z_upper, dlos)
 
     # convert A surv to on sky width
     Lindeg = np.sqrt(Asurv)
@@ -159,7 +160,7 @@ def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
 
     return 4.*np.pi*k**2 * deltak / Vfund
 
-def _calc_snr_(zst, P21, Pdelta, P21delta_deriv, N21, Nmodes, b, I, sigma=4E4, wave_emit=0.65628):
+def _calc_snr_(zst, P21, Pdelta, P21delta_deriv, N21, Nmodes, b, I, sigma=4E4, wave_emit=0.65628, returnvar21=False):
     wave_obs = (1.+zst)*wave_emit
     Vpix = calc_vpix(wave_obs)
     NHa = sigma**2 * Vpix
@@ -176,9 +177,12 @@ def _calc_snr_(zst, P21, Pdelta, P21delta_deriv, N21, Nmodes, b, I, sigma=4E4, w
     P21i_deriv = b * I * P21delta_deriv
 
     varz = varP21i / (P21i_deriv**2)
-    return np.sqrt(varz/Nmodes)
+    if returnvar21:
+        return np.sqrt(varP21i/Nmodes)
+    else:
+        return np.sqrt(varz/Nmodes)
 
-def snr_wrapper(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, deltaz, b=4):
+def snr_wrapper(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, deltaz, b=4, returnvar21=False):
     keval = (kmin+kmax)/2.0
     deltak = kmax - kmin
 
@@ -202,8 +206,11 @@ def snr_wrapper(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, deltaz, b=4):
     Nm = Nmodes(keval, deltak, zst, deltaz)
     print(Nm)
 
-    sigmazst = _calc_snr_(zst, P21, Pdelta, Pderiv, N21, Nm, b, I)
-    return float(sigmazst)
+    sigmazst = _calc_snr_(zst, P21, Pdelta, Pderiv, N21, Nm, b, I, returnvar21=returnvar21)
[…]

### 2019-08-15 plots/helper.py
Add Hbeta option to Halpha_intensity

@@ -113,7 +113,7 @@ def compute_power_spectrum(field, Lbox, npix, kmin=None, kmax=None, deltak=1.4):
 
     return klist, Pklist
 
-def Halpha_intensity(z):
+def Halpha_intensity(z, Hbeta=False):
     def psi(zp):
         ans = 0.015
         ans *= (1+zp)**(2.7)
@@ -126,7 +126,11 @@ def Halpha_intensity(z):
     nurest_Ha = c/(656.28 * u.nm)
 
     ans = (L0*psi_at_z / (4.*np.pi*nurest_Ha)) * (c/Hz)
-    return ans.to_value(u.Jy)
+    ans = ans.to_value(u.Jy)
+    if Hbeta:
+        return ans * 0.35
+    else:
+        return ans
 
 def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
     dlambda = wave_obs/R

### 2019-08-15 plots/helper.py
Update helper.py

@@ -208,11 +208,10 @@ def snr_wrapper(zst, zlist, klist, xps, pdelta, p21, kmin, kmax, deltaz, b=4, re
     N21 = fn_p21(zst, 0.1)
 
     Nm = Nmodes(keval, deltak, zst, deltaz)
-    print(Nm)
 
     sigmazst = _calc_snr_(zst, P21, Pdelta, Pderiv, N21, Nm, b, I, returnvar21=returnvar21)
     if returnvar21:
-        return float(sigmazst), P21
+        return float(sigmazst), xps
     else:
         return float(sigmazst), zst
 
@@ -233,4 +232,6 @@ if __name__ == '__main__':
     zlist, klist, xps, pdelta, p21 = read_xps(directory+'/xps*', return_auto=True)
 
     sigmazst = add_snr_in_quadrature(10, zlist, klist, xps, pdelta, p21, 0.1, 1.0, 10, 0.1)
-    sigmap21, P21 = snr_wrapper(10, zlist, klist, xps, pdelta, p21, 0.1, 0.2, 0.1, returnvar21=True)
+    sigmap21, this_xps, P21, Pi, Pdelta = snr_wrapper(10, zlist, klist, xps, pdelta, p21, 0.1, 0.2, 0.1, returnvar21=True)
+
+    # sigmap21, P21 = snr_wrapper(10, zlist, klist, xps, pdelta, p21, 0.1, 0.2, 0.1, sigma=)

### 2019-08-15 plots/ztran_vs_k/plot_ztran_vs_k.py
Small changes to ztran plot

@@ -32,6 +32,8 @@ for name, directory, c in zip(name_list, dir_list, color_list):
     zlist, klist, xps = read_xps(directory+'/xps*')
     klist, ztran = find_ztran(zlist, klist, xps)
 
+    print(ztran)
+
     ax.plot(klist, ztran, label=name, c=c)
 
 ax.set_xscale('log')
@@ -39,11 +41,11 @@ ax.set_xscale('log')
 ax.set_xlim(0.1, 1.0)
 ax.set_ylim(9, 12)
 
-ax.set_xlabel(r'$k\,[\,h\text{Mpc}^{-1}\,]$')
+ax.set_xlabel(r'$k\,[\,text{Mpc}^{-1}\,]$')
 ax.set_ylabel(r'$z_{\star}$')
 
-ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
-ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
+# ax.xaxis.set_major_formatter(FormatStrFormatter('%.1f'))
+# ax.xaxis.set_minor_formatter(FormatStrFormatter('%.1f'))
 
 ax.legend(title='model', frameon=False)
 fig.tight_layout()

### 2019-08-15 paper/ms.tex
Update authors

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[A. Beane, K. Moriwaki, ...]{
-Angus Beane$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu},
-Kana Moriwaki$^{2}$,
+\author[A. Beane et al.]{
+Angus Beane,$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu}
+Adam Lidz,$^{2}$
+Kana Moriwaki,$^{3}$
 and others
@@
 $^{1}$Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{2}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan
+$^{2}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA\\
+$^{3}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan
 % $^{2}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA\\
-% $^{3}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA
 }

### 2019-08-15 paper/ms.tex
Small text edits

@@
 are sensitive to the detailed formation of the first galaxies. An important
-transition occurs on large scales at $\avg{x_i}\sim0.15$, when the 21~cm field
-transitions from being positively correlated with the galaxy field to being
+transition occurs on large scales at $z\sim10$, when the 21~cm field
+transitions from being positively correlated with the density field to being
 negatively correlated. The redshift at which this transition occurs (the
-``transition redshift'') is, in principle, sensitive to both the structure of
-the 21~cm field but also the galaxy field. However, by considering a fixed
-model for the EoR and varying the parameters of a simple model for the galaxy
-field in a mock [O~\textsc{iii}]-emitter sample cross-correlation, we show
-that the transition redshift is in fact insensitive to the structure of the
-selected galaxy sample. We show that prospects for measuring the transition
-redshift are feasible in the near-term with a combination of LOFAR and JWST.
-Being derived from a cross-correlation, the transition redshift is less
-impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
-measurements. Therefore, the transition redshift is an interesting probe of
-the early stages of the EoR, and its detectability and interpretability
-deserve further study.
+``transition redshift'') is in principle measurable if the 21~cm field can be
+cross-correlated with a tracer of the density field (such as galaxies or a
+line intensity map) at that high redshift. Since the transition redshift is
+derived from a cross-correlation, it is in principle sensitive to the
+structure of both the 21~cm field and the tracer used to measure it. However,
+by considering a fixed model for the EoR and varying the parameters of a
+simple model for a H$\alpha$ intensity map cross-correlation, we show that the
+transition redshift is in fact very insensitive to the structure of the
+density tracer. A simple analytic argument motivates this result. We show that
+prospects for measuring the transition redshift are feasible in the near-term
+with a combination of LOFAR and JWST. Being derived from a cross-correlation,
+the transition redshift is less impacted by foreground contamination currently
+inhibiting 21~cm auto-spectrum measurements. Therefore, the transition
+redshift is an interesting probe of the early stages of the EoR, and its
+detectability and interpretability deserve further study.
 \end{abstract}

### 2019-08-16 plots/helper.py
Update Halpha_intensity

@@ -114,6 +114,13 @@ def compute_power_spectrum(field, Lbox, npix, kmin=None, kmax=None, deltak=1.4):
     return klist, Pklist
 
 def Halpha_intensity(z, Hbeta=False):
+    if Hbeta:
+        wave = 486.13615 * u.nm
+        L0 = 0.35 * 3.29E7 * u.Lsun / (u.Msun/u.year)
+    else:
+        wave = 656.45377 * u.nm
+        L0 = 3.29E7 * u.Lsun / (u.Msun/u.year)
+
     def psi(zp):
         ans = 0.015
         ans *= (1+zp)**(2.7)
@@ -121,16 +128,12 @@ def Halpha_intensity(z, Hbeta=False):
         return ans
 
     psi_at_z = psi(z) * u.Msun/u.year/(u.Mpc**3)
-    L0 = 3.29E7 * u.Lsun / (u.Msun/u.year)
     Hz = cosmo.Hz(z) * u.km/u.s/u.Mpc
-    nurest_Ha = c/(656.28 * u.nm)
+    nurest = c/wave
 
-    ans = (L0*psi_at_z / (4.*np.pi*nurest_Ha)) * (c/Hz)
+    ans = (L0*psi_at_z / (4.*np.pi*nurest)) * (c/Hz)
     ans = ans.to_value(u.Jy)
-    if Hbeta:
-        return ans * 0.35
-    else:
-        return ans
+    return ans
 
 def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
     dlambda = wave_obs/R
@@ -232,6 +235,6 @@ if __name__ == '__main__':
     zlist, klist, xps, pdelta, p21 = read_xps(directory+'/xps*', return_auto=True)
 
     sigmazst = add_snr_in_quadrature(10, zlist, klist, xps, pdelta, p21, 0.1, 1.0, 10, 0.1)
-    sigmap21, this_xps, P21, Pi, Pdelta = snr_wrapper(10, zlist, klist, xps, pdelta, p21, 0.1, 0.2, 0.1, returnvar21=True)
+    sigmap21, this_xps = snr_wrapper(10, zlist, klist, xps, pdelta, p21, 0.1, 0.2, 0.1, returnvar21=True)
 
     # sigmap21, P21 = snr_wrapper(10, zlist, klist, xps, pdelta, p21, 0.1, 0.2, 0.1, sigma=)

### 2019-08-16 plots/noise.py
Create noise.py

@@ -1,0 +1,40 @@
+import glob
+import numpy as np
+import re
+from scipy.interpolate import interp1d, interp2d
+from scipy.optimize import ridder
+
+import astropy.units as u
+from astropy.constants import c
+from scipy.interpolate import interp2d
+
+from colossus.cosmology import cosmology
+from helper import read_xps
+
+params = {'flat': True, 'H0': 67.66, 'Om0': 0.3111, 'Ob0': 0.02242/(0.6766**2), 'sigma8': 0.8102, 'ns': 0.9665}
+cosmo = cosmology.setCosmology('myCosmo', params)
+
+h = 0.6766
+
+def Halpha_intensity(z, Hbeta=False):
+    if Hbeta:
+        wave = 486.13615 * u.nm
+        L0 = 0.35 * 3.29E7 * u.Lsun / (u.Msun/u.year)
+    else:
+        wave = 656.45377 * u.nm
+        L0 = 3.29E7 * u.Lsun / (u.Msun/u.year)
+
+    def psi(zp):
+        ans = 0.015
+        ans *= (1+zp)**(2.7)
+        ans /= 1 + ((1+zp)/2.9)**(5.6)
+        return ans
+
+    psi_at_z = psi(z) * u.Msun/u.year/(u.Mpc**3)
+    Hz = cosmo.Hz(z) * u.km/u.s/u.Mpc
+    nurest = c/wave
+
+    ans = (L0*psi_at_z / (4.*np.pi*nurest)) * (c/Hz)
+    ans = ans.to_value(u.Jy)
+    return ans
+

### 2019-08-16 plots/noise.py
Add computation of Nx

@@ -38,3 +38,8 @@ def Halpha_intensity(z, Hbeta=False):
     ans = ans.to_value(u.Jy)
     return ans
 
+def compute_Nx(wave_obs, sigma=4E4, wave_emit=0.65628):
+    vpix = calc_vpix(wave_obs, wave_emit=wave_emit)
+    ans = sigma**2 * vpix
+    return ans
+

### 2019-08-16 plots/noise.py
Add Nmodes (from helper)

@@ -43,3 +43,17 @@ def compute_Nx(wave_obs, sigma=4E4, wave_emit=0.65628):
     ans = sigma**2 * vpix
     return ans
 
+def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
+    z_upper = z + deltaz/2.0
+    z_lower = z - deltaz/2.0
+    dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
+    print(z, deltaz, z_lower, z_upper, dlos)
+
+    # convert A surv to on sky width
+    Lindeg = np.sqrt(Asurv)
+    Lperp = cosmo.angularDiameterDistance(z)/cosmo.h * Lindeg * (np.pi/180.)
+
+    Vfund = (2.*np.pi)**3 / (Lperp**2 * dlos)
+
+    return 4.*np.pi*k**2 * deltak / Vfund
+

### 2019-08-16 plots/noise.py
Add correct vpix function

@@ -57,3 +57,23 @@ def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
 
     return 4.*np.pi*k**2 * deltak / Vfund
 
+def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
+    # compute the upper and lower redshift from the spectrograph resolution
+    dlambda = wave_obs/R
+    wave_upper = wave_obs + dlambda/2.0
+    wave_lower = wave_obs - dlambda/2.0
+
+    z_upper = (wave_upper-wave_emit)/wave_emit
+    z_lower = (wave_lower-wave_emit)/wave_emit
+
+    d_upper = cosmo.comovingDistance(z_max=z_upper)/cosmo.h
+    d_lower = cosmo.comovingDistance(z_max=z_lower)/cosmo.h
+    volume = (4.*np.pi/3.) * (d_upper**3 - d_lower**3)
+
+    Apix = (pix_length_in_arcsecond * u.arcsecond)**2
+    Apix = Apix.to_value(u.deg**2)
+    tot_sky_in_degree = (4.*np.pi * u.steradian).to_value(u.deg**2)
+    Apix_fraction = Apix / tot_sky_in_degree
+
+    return Apix_fraction * volume
+

### 2019-08-16 plots/noise.py
Add function that will construct interpolators

@@ -77,3 +77,10 @@ def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
 
     return Apix_fraction * volume
 
+def construct_interpolators(zlist, klist, xps, pdelta, p21):
+    fn_xps = interp2d(zlist, klist, np.transpose(xps))
+    fn_pdelta = interp2d(zlist, klist, np.transpose(pdelta))
+    fn_p21 = interp2d(zlist, klist, np.transpose(p21))
+
+    return fn_xps, fn_pdelta, fn_p21
+

### 2019-08-16 plots/noise.py
Add small function which will compute varp21x

@@ -84,3 +84,9 @@ def construct_interpolators(zlist, klist, xps, pdelta, p21):
 
     return fn_xps, fn_pdelta, fn_p21
 
+def varp21x(P21, N21, Px, Nx):
+    xps = np.sqrt(P21*Px)
+    P21tot = P21 + N21
+    Pxtot = Px + Nx
+    return xps**2 + P21tot*Pxtot
+

### 2019-08-16 plots/noise.py
Add wrapper over varp21x function

@@ -90,3 +90,26 @@ def varp21x(P21, N21, Px, Nx):
     Pxtot = Px + Nx
     return xps**2 + P21tot*Pxtot
 
+def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
+    fn_xps, fn_pdelta, fn_p21 = construct_interpolators(zlist, klist, xps, pdelta, p21)
+
+    kcen = (kmin+kmax)/2.0
+    deltak = kmax-kmin
+
+    P21 = fn_p21(z, kcen)
+
+    Ix = Halpha_intensity(z)
+    Px = (b*Ix)**2 * fn_pdelta(z, kcen)
+
+    wave_obs_x = wave_emit_x*(1.+z)
+
+    N21 = fn_p21(z, 0.1)
+    Nx = compute_Nx(wave_obs_x, sigma=sigma)
+
+    varxps = varp21x(P21, N21, Px, Nx)
+    Nm = Nmodes(kcen, deltak, z, deltaz)
+    xps = np.sqrt(P21*Px)
+
+    return float(xps), float(np.sqrt(varxps/Nm))
+
+

### 2019-08-16 plots/noise.py
Add some readin

@@ -113,3 +113,6 @@ def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
     return float(xps), float(np.sqrt(varxps/Nm))
 
 
+if __name__ == '__main__':
+    directory = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256/fid/MyOutput'
+    zlist, klist, xps, pdelta, p21 = read_xps(directory+'/xps*', return_auto=True)

### 2019-08-23 plots/mcmc_logistic/test.py
Add some mcmc test

@@ -1,0 +1,68 @@
+import sys
+sys.path.append('../')
+from helper import read_xps, find_ztran
+
+import numpy as np
+import emcee
+from scipy.interpolate import interp2d
+
+import matplotlib.pyplot as plt
+import corner
+
+zmin = 7
+zmax = 15
+
+def lnprior(theta):
+    m, z0 = theta
+    if m > 0.0 and zmin < z0 < zmax:
+        return 0.0
+    return -np.inf
+
+def lnlike(theta, zlist, Plist, sigma):
+    m, z0 = theta
+    model = m*(zlist-z0)
+    return -0.5 * np.sum(np.divide(np.square(np.subtract(Plist, model)), np.square(sigma)))
+
+def lnprob(theta, zlist, Plist, sigma):
+    lp = lnprior(theta)
+    if not np.isfinite(lp):
+        return -np.inf
+    return lp + lnlike(theta, zlist, Plist, sigma)
+
+directory = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256/fid/MyOutput'
+zlist, klist, xps, pdelta, p21 = read_xps(directory+'/xps*', return_auto=True)
+ztran_klist, ztran = find_ztran(zlist, klist, xps)
+our_ztran = ztran[5]
+print(our_ztran)
+
+fn_xps = interp2d(zlist, klist, np.transpose(xps))
+
+zlist = np.arange(zmin, zmax, 0.4)
+truth = fn_xps(zlist, 0.1)
+data = np.random.normal(loc=truth, scale=5*np.abs(truth[-1]))
+
+sigma = 5 * np.abs(truth[-1])
+sigma = np.full(len(truth), sigma)
+
+ndim, nwalkers = 2, 100
+mlist = np.abs(2000.0*np.random.rand(nwalkers))
+this_zlist = np.random.normal(our_ztran, 1, nwalkers)
+pos = np.transpose([mlist, this_zlist])
+
+sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(zlist, data, sigma))
+sampler.run_mcmc(pos, 10000)
+
+samples = sampler.chain[:, 2000:, :].reshape((-1, ndim))
+
+fig = corner.corner(samples, labels=['m', 'z0'], truths=[2000, our_ztran])
+fig.savefig("test.png")
+
+plt.close()
+
+plt.plot(zlist, truth)
[…]

### 2019-08-23 plots/noise.py
Add a more general line intensity function

@@ -16,6 +16,31 @@ cosmo = cosmology.setCosmology('myCosmo', params)
 
 h = 0.6766
 
+def line_intensity(z, line):
+    if line == 'Halpha':
+        wave = 656.45377 * u.nm
+        L0 = 3.29E7 * u.Lsun / (u.Msun/u.year)
+    elif line == 'Hbeta':
+        wave = 486.13615 * u.nm
+        L0 = 0.35 * 3.29E7 * u.Lsun / (u.Msun/u.year)
+    elif line == 'Lyalpha':
+        wave = 121.567 * u.nm
+        L0 = 2.859E8 * u.Lsun / (u.Msun/u.year)       
+
+    def psi(zp):
+        ans = 0.015
+        ans *= (1+zp)**(2.7)
+        ans /= 1 + ((1+zp)/2.9)**(5.6)
+        return ans
+
+    psi_at_z = psi(z) * u.Msun/u.year/(u.Mpc**3)
+    Hz = cosmo.Hz(z) * u.km/u.s/u.Mpc
+    nurest = c/wave
+
+    ans = (L0*psi_at_z / (4.*np.pi*nurest)) * (c/Hz)
+    ans = ans.to_value(u.Jy)
+    return ans
+
 def Halpha_intensity(z, Hbeta=False):
     if Hbeta:
         wave = 486.13615 * u.nm

### 2019-08-23 plots/noise.py
Change Nmodes to kmin and kmax args

@@ -68,19 +68,19 @@ def compute_Nx(wave_obs, sigma=4E4, wave_emit=0.65628):
     ans = sigma**2 * vpix
     return ans
 
-def Nmodes(k, deltak, z, deltaz, Asurv=31.1):
+def Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
     z_upper = z + deltaz/2.0
     z_lower = z - deltaz/2.0
     dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
-    print(z, deltaz, z_lower, z_upper, dlos)
 
     # convert A surv to on sky width
     Lindeg = np.sqrt(Asurv)
     Lperp = cosmo.angularDiameterDistance(z)/cosmo.h * Lindeg * (np.pi/180.)
 
     Vfund = (2.*np.pi)**3 / (Lperp**2 * dlos)
+    Vkspace = (4*np.pi/3.) * (kmax**3 - kmin**3)
 
-    return 4.*np.pi*k**2 * deltak / Vfund
+    return Vkspace / Vfund
 
 def calc_vpix(wave_obs, pix_length_in_arcsecond=1, R=300, wave_emit=0.65628):
     # compute the upper and lower redshift from the spectrograph resolution
@@ -132,7 +132,7 @@ def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
     Nx = compute_Nx(wave_obs_x, sigma=sigma)
 
     varxps = varp21x(P21, N21, Px, Nx)
-    Nm = Nmodes(kcen, deltak, z, deltaz)
+    Nm = Nmodes(kmin, kmax, z, deltaz)
     xps = np.sqrt(P21*Px)
 
     return float(xps), float(np.sqrt(varxps/Nm))

### 2019-08-23 plots/noise.py
Add summation over k bins

@@ -137,6 +137,18 @@ def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
 
     return float(xps), float(np.sqrt(varxps/Nm))
 
+def sum_var_over_bins(z, deltaz, kmin, kmax, Nk, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
+    kbins = np.linspace(kmin, kmax, Nk)
+    totsnr = 0.0
+    for i in range(len(kbins)-1):
+        this_kmin = kbins[i]
+        this_kmax = kbins[i+1]
+        this_xps, this_stdxps = varp21x_wrapper(z, deltaz, this_kmin, this_kmax, zlist, klist, xps, pdelta, p21,
+                                                b=b, sigma=sigma, wave_emit_x=wave_emit_x)
+
+        totsnr += np.square(this_xps/this_stdxps)
+    return np.sqrt(totsnr)
+
 
 if __name__ == '__main__':
     directory = '/Users/abeane/scratch/ztran_OIII_sims/v1.2/256Mpch/256/fid/MyOutput'

### 2019-08-23 plots/noise.py
Update to use new line_intensity function

@@ -115,7 +115,7 @@ def varp21x(P21, N21, Px, Nx):
     Pxtot = Px + Nx
     return xps**2 + P21tot*Pxtot
 
-def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
+def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
     fn_xps, fn_pdelta, fn_p21 = construct_interpolators(zlist, klist, xps, pdelta, p21)
 
     kcen = (kmin+kmax)/2.0
@@ -123,7 +123,7 @@ def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
 
     P21 = fn_p21(z, kcen)
 
-    Ix = Halpha_intensity(z)
+    Ix = line_intensity(line, z)
     Px = (b*Ix)**2 * fn_pdelta(z, kcen)
 
     wave_obs_x = wave_emit_x*(1.+z)
@@ -137,13 +137,13 @@ def varp21x_wrapper(z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
 
     return float(xps), float(np.sqrt(varxps/Nm))
 
-def sum_var_over_bins(z, deltaz, kmin, kmax, Nk, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
+def sum_var_over_bins(line, z, deltaz, kmin, kmax, Nk, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
     kbins = np.linspace(kmin, kmax, Nk)
     totsnr = 0.0
     for i in range(len(kbins)-1):
         this_kmin = kbins[i]
         this_kmax = kbins[i+1]
-        this_xps, this_stdxps = varp21x_wrapper(z, deltaz, this_kmin, this_kmax, zlist, klist, xps, pdelta, p21,
+        this_xps, this_stdxps = varp21x_wrapper(line, z, deltaz, this_kmin, this_kmax, zlist, klist, xps, pdelta, p21,
                                                 b=b, sigma=sigma, wave_emit_x=wave_emit_x)
 
         totsnr += np.square(this_xps/this_stdxps)

### 2019-08-23 plots/noise.py
Improve error handling for line_intensity

@@ -17,6 +17,8 @@ cosmo = cosmology.setCosmology('myCosmo', params)
 h = 0.6766
 
 def line_intensity(z, line):
+    assert isinstance(line, str), "line must be a string!"
+
     if line == 'Halpha':
         wave = 656.45377 * u.nm
         L0 = 3.29E7 * u.Lsun / (u.Msun/u.year)
@@ -25,7 +27,9 @@ def line_intensity(z, line):
         L0 = 0.35 * 3.29E7 * u.Lsun / (u.Msun/u.year)
     elif line == 'Lyalpha':
         wave = 121.567 * u.nm
-        L0 = 2.859E8 * u.Lsun / (u.Msun/u.year)       
+        L0 = 2.859E8 * u.Lsun / (u.Msun/u.year)
+    else:
+        raise Exception('cant recognize line: '+str(line))   
 
     def psi(zp):
         ans = 0.015

### 2019-08-23 plots/noise.py
Fix call to line_intensity

@@ -127,7 +127,7 @@ def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21,
 
     P21 = fn_p21(z, kcen)
 
-    Ix = line_intensity(line, z)
+    Ix = line_intensity(z, line)
     Px = (b*Ix)**2 * fn_pdelta(z, kcen)
 
     wave_obs_x = wave_emit_x*(1.+z)

### 2019-08-23 plots/noise.py
Add observed wavelength print statement for convenience

@@ -131,6 +131,7 @@ def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21,
     Px = (b*Ix)**2 * fn_pdelta(z, kcen)
 
     wave_obs_x = wave_emit_x*(1.+z)
+    print('observed wavelength: ', wave_obs_x)
 
     N21 = fn_p21(z, 0.1)
     Nx = compute_Nx(wave_obs_x, sigma=sigma)

### 2019-08-23 plots/mcmc_logistic/test.py
Change to 25% for mcmc

@@ -39,7 +39,7 @@ fn_xps = interp2d(zlist, klist, np.transpose(xps))
 
 zlist = np.arange(zmin, zmax, 0.4)
 truth = fn_xps(zlist, 0.1)
-data = np.random.normal(loc=truth, scale=5*np.abs(truth[-1]))
+data = np.random.normal(loc=truth, scale=4*np.abs(truth[-1]))
 
 sigma = 5 * np.abs(truth[-1])
 sigma = np.full(len(truth), sigma)

### 2019-08-23 plots/noise.py
Make Asurv user-definable

@@ -119,7 +119,8 @@ def varp21x(P21, N21, Px, Nx):
     Pxtot = Px + Nx
     return xps**2 + P21tot*Pxtot
 
-def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
+def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
+                    sigma=4E4, wave_emit_x=0.65628, Asurv=31.1):
     fn_xps, fn_pdelta, fn_p21 = construct_interpolators(zlist, klist, xps, pdelta, p21)
 
     kcen = (kmin+kmax)/2.0
@@ -137,19 +138,20 @@ def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21,
     Nx = compute_Nx(wave_obs_x, sigma=sigma)
 
     varxps = varp21x(P21, N21, Px, Nx)
-    Nm = Nmodes(kmin, kmax, z, deltaz)
+    Nm = Nmodes(kmin, kmax, z, deltaz, Asurv=Asurv)
     xps = np.sqrt(P21*Px)
 
     return float(xps), float(np.sqrt(varxps/Nm))
 
-def sum_var_over_bins(line, z, deltaz, kmin, kmax, Nk, zlist, klist, xps, pdelta, p21, b=4, sigma=4E4, wave_emit_x=0.65628):
+def sum_var_over_bins(line, z, deltaz, kmin, kmax, Nk, zlist, klist, xps, pdelta, p21, b=4, 
+                      sigma=4E4, wave_emit_x=0.65628, Asurv=31.1):
     kbins = np.linspace(kmin, kmax, Nk)
     totsnr = 0.0
     for i in range(len(kbins)-1):
         this_kmin = kbins[i]
         this_kmax = kbins[i+1]
         this_xps, this_stdxps = varp21x_wrapper(line, z, deltaz, this_kmin, this_kmax, zlist, klist, xps, pdelta, p21,
-                                                b=b, sigma=sigma, wave_emit_x=wave_emit_x)
+                                                b=b, sigma=sigma, wave_emit_x=wave_emit_x, Asurv=Asurv)
 
         totsnr += np.square(this_xps/this_stdxps)
     return np.sqrt(totsnr)

### 2019-08-23 plots/noise.py
Remove necessity to specify emitted wavelength, add k at which N21=P21

@@ -120,7 +120,18 @@ def varp21x(P21, N21, Px, Nx):
     return xps**2 + P21tot*Pxtot
 
 def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21, b=4, 
-                    sigma=4E4, wave_emit_x=0.65628, Asurv=31.1):
+                    sigma=4E4, Asurv=31.1, k21=0.1):
+    assert isinstance(line, str), "line must be a string!"
+
+    if line == 'Halpha':
+        wave_emit_x = 0.65645377
+    elif line == 'Hbeta':
+        wave_emit_x = 0.48613615
+    elif line == 'Lyalpha':
+        wave_emit_x = 0.121567
+    else:
+        raise Exception('cant recognize line: '+str(line))   
+
     fn_xps, fn_pdelta, fn_p21 = construct_interpolators(zlist, klist, xps, pdelta, p21)
 
     kcen = (kmin+kmax)/2.0
@@ -134,7 +145,7 @@ def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21,
     wave_obs_x = wave_emit_x*(1.+z)
     print('observed wavelength: ', wave_obs_x)
 
-    N21 = fn_p21(z, 0.1)
+    N21 = fn_p21(z, k21)
     Nx = compute_Nx(wave_obs_x, sigma=sigma)
 
     varxps = varp21x(P21, N21, Px, Nx)
@@ -144,14 +155,14 @@ def varp21x_wrapper(line, z, deltaz, kmin, kmax, zlist, klist, xps, pdelta, p21,
     return float(xps), float(np.sqrt(varxps/Nm))
 
 def sum_var_over_bins(line, z, deltaz, kmin, kmax, Nk, zlist, klist, xps, pdelta, p21, b=4, 
-                      sigma=4E4, wave_emit_x=0.65628, Asurv=31.1):
+                      sigma=4E4, Asurv=31.1, k21=0.1):
     kbins = np.linspace(kmin, kmax, Nk)
     totsnr = 0.0
     for i in range(len(kbins)-1):
         this_kmin = kbins[i]
         this_kmax = kbins[i+1]
         this_xps, this_stdxps = varp21x_wrapper(line, z, deltaz, this_kmin, this_kmax, zlist, klist, xps, pdelta, p21,
[…]

### 2019-08-23 plots/noise.py
Create noise.py, add average line intensity function

@@ -1,0 +1,46 @@
+import numpy as np
+
+import astropy.units as u
+from astropy.constants import c
+
+from colossus.cosmology import cosmology
+
+params = {'flat': True, 'H0': 67.66, 'Om0': 0.3111, 'Ob0': 0.02242/(0.6766**2), 'sigma8': 0.8102, 'ns': 0.9665}
+cosmo = cosmology.setCosmology('myCosmo', params)
+
+line_wavelength = {'Halpha': 656.45377 * u.nm,
+                   'Hbeta': 486.13615 * u.nm,
+                   'Lyalpha': 121.567 * u.nm}
+
+line_L0 = {'Halpha': 3.29E7 * u.Lsun / (u.Msun/u.year),
+           'Hbeta': 0.35 * 3.29E7 * u.Lsun / (u.Msun/u.year),
+           'Lyalpha': 2.859E8 * u.Lsun / (u.Msun/u.year)}
+
+def psi(zp):
+    ans = 0.015
+    ans *= (1+zp)**(2.7)
+    ans /= 1 + ((1+zp)/2.9)**(5.6)
+    return ans * u.Msun/(u.year * u.Mpc**3)
+
+def line_intensity(z, line, surface_brightness=True):
+    assert isinstance(line, str), "line must be a string!"
+    assert line in line_wavelength.keys(), "line: "+line+" not recognized!"
+
+    wave = line_wavelength[line]
+    L0 = line_L0[line]
+
+    psi_at_z = psi(z)
+    Hz = cosmo.Hz(z) * u.km/u.s/u.Mpc
+    nurest = c/wave
+    nuobs = nurest / (1. + z)
+
+    ans = (L0*psi_at_z / (4.*np.pi*nurest)) * (c/Hz) / (1. * u.sr)
+    
+    if surface_brightness:
+        ans *= nuobs
+        ans = ans.to(u.erg/u.cm**2/u.s/u.sr)
+    else:
+        ans = ans.to(u.erg/u.cm**2/u.s/u.sr/u.Hz)
+
+    return ans
+

### 2019-08-23 plots/noise.py
Create intensity power spectrum function

@@ -44,3 +44,17 @@ def line_intensity(z, line, surface_brightness=True):
 
     return ans
 
+def intensity_power_spectrum(z, k, I=None, line=None, b=4, dimensionless=True, surface_brightness=True):
+    Pden = cosmo.matterPowerSpectrum(k.to_value(1/u.Mpc)/cosmo.h, z)/(cosmo.h**3)
+    Pden *= u.Mpc**3
+
+    if I is None:
+        assert line is not None, "If I is not specified you must specify the line"
+        I = line_intensity(z, line, surface_brightness=surface_brightness)
+
+    ans = (b*I)**2 * Pden
+
+    if dimensionless:
+        ans *= k**3 / (2.*np.pi**2)
+
+    return ans

### 2019-08-23 plots/noise.py
Add vpix calculator

@@ -58,3 +58,24 @@ def intensity_power_spectrum(z, k, I=None, line=None, b=4, dimensionless=True, s
         ans *= k**3 / (2.*np.pi**2)
 
     return ans
+
+def calc_vpix(wave_obs, wave_emit, pix_length_in_arcsecond=1, R=300):
+    # compute the upper and lower redshift from the spectrograph resolution
+    dlambda = wave_obs/R
+    wave_upper = wave_obs + dlambda/2.0
+    wave_lower = wave_obs - dlambda/2.0
+
+    z_upper = ((wave_upper-wave_emit)/wave_emit).to_value(u.dimensionless_unscaled)
+    z_lower = (wave_lower-wave_emit)/wave_emit.to_value(u.dimenisonless_unscaled)
+
+    d_upper = cosmo.comovingDistance(z_max=z_upper)/cosmo.h
+    d_lower = cosmo.comovingDistance(z_max=z_lower)/cosmo.h
+    volume = (4.*np.pi/3.) * (d_upper**3 - d_lower**3)
+
+    Apix = (pix_length_in_arcsecond * u.arcsecond)**2
+    Apix = Apix.to_value(u.deg**2)
+    tot_sky_in_degree = (4.*np.pi * u.steradian).to_value(u.deg**2)
+    Apix_fraction = Apix / tot_sky_in_degree
+
+    return Apix_fraction * volume
+

### 2019-08-23 plots/noise.py
Add Nmodes calculator

@@ -79,3 +79,17 @@ def calc_vpix(wave_obs, wave_emit, pix_length_in_arcsecond=1, R=300):
 
     return Apix_fraction * volume
 
+def calc_Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
+    z_upper = z + deltaz/2.0
+    z_lower = z - deltaz/2.0
+    dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
+
+    # convert A surv to on sky width
+    Lindeg = np.sqrt(Asurv)
+    Lperp = cosmo.angularDiameterDistance(z)/cosmo.h * Lindeg * (np.pi/180.)
+
+    Vfund = (2.*np.pi)**3 / (Lperp**2 * dlos)
+    Vkspace = (4*np.pi/3.) * (kmax**3 - kmin**3)
+
+    return Vkspace / Vfund
+

### 2019-08-23 plots/noise.py
Add Nx calculator

@@ -93,3 +93,8 @@ def calc_Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
 
     return Vkspace / Vfund
 
+def compute_Nx(wave_obs, wave_emit, sigma):
+    vpix = calc_vpix(wave_obs, wave_emit)
+    ans = sigma**2 * vpix
+    return ans
+

### 2019-08-23 plots/noise.py
Add single-mode var calculator

@@ -98,3 +98,6 @@ def compute_Nx(wave_obs, wave_emit, sigma):
     ans = sigma**2 * vpix
     return ans
 
+def _var_auto_singlemode(P, N):
+    Ptot = P + N
+    return np.square(Ptot)

### 2019-08-25 plots/noise.py
Fix astropy units handling

@@ -77,12 +77,15 @@ def calc_vpix(wave_obs, wave_emit, pix_length_in_arcsecond=1, R=300):
     tot_sky_in_degree = (4.*np.pi * u.steradian).to_value(u.deg**2)
     Apix_fraction = Apix / tot_sky_in_degree
 
-    return Apix_fraction * volume
+    return Apix_fraction * volume * u.Mpc**3
 
 def calc_Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
     z_upper = z + deltaz/2.0
     z_lower = z - deltaz/2.0
     dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
+
+    kmin = kmin.to(1/u.Mpc)
+    kmax = kmax.to(1/u.Mpc)
 
     # convert A surv to on sky width
     Lindeg = np.sqrt(Asurv)

### 2019-08-26 plots/noise.py
Change method of computing Vpix

@@ -66,18 +66,19 @@ def calc_vpix(wave_obs, wave_emit, pix_length_in_arcsecond=1, R=300):
     wave_lower = wave_obs - dlambda/2.0
 
     z_upper = ((wave_upper-wave_emit)/wave_emit).to_value(u.dimensionless_unscaled)
-    z_lower = (wave_lower-wave_emit)/wave_emit.to_value(u.dimenisonless_unscaled)
+    z_lower = ((wave_lower-wave_emit)/wave_emit).to_value(u.dimensionless_unscaled)
+    z = (wave_obs/wave_emit).to_value(u.dimensionless_unscaled) - 1
 
-    d_upper = cosmo.comovingDistance(z_max=z_upper)/cosmo.h
-    d_lower = cosmo.comovingDistance(z_max=z_lower)/cosmo.h
-    volume = (4.*np.pi/3.) * (d_upper**3 - d_lower**3)
+    d_upper = cosmo.comovingDistance(z_max=z_upper)/cosmo.h * u.Mpc
+    d_lower = cosmo.comovingDistance(z_max=z_lower)/cosmo.h * u.Mpc
+    dpar = d_upper - d_lower
+    print(dpar, cosmo.comovingDistance(z_lower, z_upper)/cosmo.h * u.Mpc)
 
-    Apix = (pix_length_in_arcsecond * u.arcsecond)**2
-    Apix = Apix.to_value(u.deg**2)
-    tot_sky_in_degree = (4.*np.pi * u.steradian).to_value(u.deg**2)
-    Apix_fraction = Apix / tot_sky_in_degree
+    xpix = (pix_length_in_arcsecond * u.arcsecond).to_value(u.radian)
+    dperp = xpix * cosmo.comovingDistance(0, z)/cosmo.h * u.Mpc
+    print(dperp)
 
-    return Apix_fraction * volume * u.Mpc**3
+    return dpar * dperp**2
 
 def calc_Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
     z_upper = z + deltaz/2.0

### 2019-08-26 plots/noise.py
Fix astropy unit handling

@@ -85,8 +85,8 @@ def calc_Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
     z_lower = z - deltaz/2.0
     dlos = cosmo.comovingDistance(z_lower, z_upper)/cosmo.h
 
-    kmin = kmin.to(1/u.Mpc)
-    kmax = kmax.to(1/u.Mpc)
+    kmin = kmin.to_value(1/u.Mpc)
+    kmax = kmax.to_value(1/u.Mpc)
 
     # convert A surv to on sky width
     Lindeg = np.sqrt(Asurv)

### 2019-08-26 plots/noise.py
Add surface brightness option to Nx

@@ -97,9 +97,11 @@ def calc_Nmodes(kmin, kmax, z, deltaz, Asurv=31.1):
 
     return Vkspace / Vfund
 
-def compute_Nx(wave_obs, wave_emit, sigma):
+def compute_Nx(wave_obs, wave_emit, sigma, surface_brightness=True):
     vpix = calc_vpix(wave_obs, wave_emit)
     ans = sigma**2 * vpix
+    if surface_brightness:
+        ans *= (c/wave_obs)**2
     return ans
 
 def _var_auto_singlemode(P, N):

### 2019-08-26 plots/noise.py
Add auto var wrapper

@@ -107,3 +107,31 @@ def compute_Nx(wave_obs, wave_emit, sigma, surface_brightness=True):
 def _var_auto_singlemode(P, N):
     Ptot = P + N
     return np.square(Ptot)
+
+def var_auto(line, z, deltaz, kmin, kmax, sigma, Asurv, b=4, return_signal=True, 
+             surface_brightness=True, dimensionless=False):
+    Nmodes = calc_Nmodes(kmin, kmax, z, deltaz, Asurv)
+
+    kcen = (kmin + kmax)/2.0
+
+    wave_emit = line_wavelength[line]
+    wave_obs = wave_emit * (1. + z)
+    freq_obs = c/wave_obs
+
+    P = intensity_power_spectrum(z, kcen, line=line, b=b, dimensionless=False, 
+                                 surface_brightness=surface_brightness)
+    N = compute_Nx(wave_obs, wave_emit, sigma, surface_brightness=surface_brightness)
+    if dimensionless:
+        P *= (kcen**3)/(2.*np.pi**2)
+        N *= (kcen**3)/(2.*np.pi**2)
+
+    print(P, N)
+    var_singlemode = _var_auto_singlemode(P, N)
+    var = var_singlemode/Nmodes
+    print(var)
+
+    if return_signal:
+        # return var.to((u.erg/u.s/u.cm**2/u.sr)**4), P.to((u.erg/u.s/u.cm**2/u.sr)**2)
+        return var, P
+    else:
+        return var.to((u.erg/u.s/u.cm**2/u.sr)**4)

### 2019-08-27 plots/mcmc_logistic/test.py
Further updates to MCMC test

@@ -39,7 +39,7 @@ fn_xps = interp2d(zlist, klist, np.transpose(xps))
 
 zlist = np.arange(zmin, zmax, 0.4)
 truth = fn_xps(zlist, 0.1)
-data = np.random.normal(loc=truth, scale=4*np.abs(truth[-1]))
+data = np.random.normal(loc=truth, scale=(4/5)*np.abs(truth))
 
 sigma = 5 * np.abs(truth[-1])
 sigma = np.full(len(truth), sigma)

### 2019-08-27 paper/ms.tex
Add utility section
Rewrite abstract

--- 2019-08-15 paper/ms.tex
@@
 are sensitive to the detailed formation of the first galaxies. An important
-transition occurs on large scales at $\avg{x_i}\sim0.15$, when the 21~cm field
-transitions from being positively correlated with the galaxy field to being
-negatively correlated. The redshift at which this transition occurs (the
-``transition redshift'') is, in principle, sensitive to both the structure of
-the 21~cm field but also the galaxy field. However, by considering a fixed
-model for the EoR and varying the parameters of a simple model for the galaxy
-field in a mock [O~\textsc{iii}]-emitter sample cross-correlation, we show
-that the transition redshift is in fact insensitive to the structure of the
-selected galaxy sample. We show that prospects for measuring the transition
-redshift are feasible in the near-term with a combination of LOFAR and JWST.
-Being derived from a cross-correlation, the transition redshift is less
-impacted by foreground contamination currently inhibiting 21~cm auto-spectrum
-measurements. Therefore, the transition redshift is an interesting probe of
-the early stages of the EoR, and its detectability and interpretability
-deserve further study.
+transition occurs on large scales at $z\sim10$, when the 21~cm field changes
+from being positively correlated with the density field to being negatively
+correlated. The redshift at which this occurs (the ``transition redshift'') is
+in principle measurable if the 21~cm field can be cross-correlated with a
+tracer of the density field (such as galaxies or a line intensity map) at that
+high redshift. Since the transition redshift is derived from a
+cross-correlation, it naively depends on the structure of the 21~cm field and
+the tracer field. However, we show that on large scales the transition
+redshift is independent of the structure of the tracer field. We verify this
+in simulations by assuming a simple model for a mock Ly$\alpha$ intensity
+mapping survey. By considering a joint measurement between the Square
+Kilometre Array and the Cosmic Dawn Intensity Mapper, we show that the
+transition redshift is measurable up until about $z\sim x$. Being derived from
+a cross-correlation, the transition redshift is less impacted by foreground
+contamination currently inhibiting 21~cm auto-spectrum measurements.
+Therefore, the transition redshift is an interesting probe of the early stages
+of the EoR, and its detectability and interpretability deserve further study.
 \end{abstract}
@@
 
+\section*{Utility}
+Some links to be saved for later
+
+Ly$\alpha$ intensity $L_0$ source:
+https://iopscience.iop.org/article/10.1088/0004-637X/743/1/65/meta
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-08-27 paper/ms.tex
Slight update to text

@@
 \citep{2018ApJ...867...26B}, along with combining the three cross-spectra with
-a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. While in
-this work we will only consider the cross-correlation between 21~cm and
-galaxies, all of what we consider is applicable to the transition redshift as
-computed by cross-correlating 21~cm with any of these emission lines.
+a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. Because the
+transition redshift is typically $\z_{\star} \sim 10$, it is unclear how much
+metal enrichment will have occurred by this early time.
 

### 2019-08-27 plots/noise.py
Add sigmaN calc

@@ -22,6 +22,24 @@ def psi(zp):
     ans /= 1 + ((1+zp)/2.9)**(5.6)
     return ans * u.Msun/(u.year * u.Mpc**3)
 
+def sigmaN(lam, IZL, tobs, epsilon, R=300, D=84*u.cm, Omegapix=(1*u.arcsecond)**2):
+    sigmaN0 = 1.37 * u.nW/u.m**2/u.sr
+    fac = (1 * u.micron)/lam
+    fac *= R/100
+    fac *= IZL/(1E3*u.nW/u.m**2/u.sr)
+    fac *= 0.126 * u.m**2/(np.pi*D**2)
+    fac *= 8.5E-10 * u.sr / (Omegapix)
+    fac *= 1E5 * u.s / (tobs)
+    fac *= 1./np.sqrt(epsilon)
+    fac = np.sqrt(fac).to_value(u.dimensionless_unscaled)
+
+    sigmaN0 *= fac
+    obs_freq = c/lam
+    sigmaN0 /= obs_freq
+
+    return sigmaN0.to(u.erg/u.s/u.cm**2/u.Hz/u.sr)
+    
+
 def line_intensity(z, line, surface_brightness=True):
     assert isinstance(line, str), "line must be a string!"
     assert line in line_wavelength.keys(), "line: "+line+" not recognized!"

### 2019-08-27 plots/noise.py
Slight touches

@@ -143,13 +143,12 @@ def var_auto(line, z, deltaz, kmin, kmax, sigma, Asurv, b=4, return_signal=True,
         P *= (kcen**3)/(2.*np.pi**2)
         N *= (kcen**3)/(2.*np.pi**2)
 
-    print(P, N)
     var_singlemode = _var_auto_singlemode(P, N)
     var = var_singlemode/Nmodes
-    print(var)
 
     if return_signal:
         # return var.to((u.erg/u.s/u.cm**2/u.sr)**4), P.to((u.erg/u.s/u.cm**2/u.sr)**2)
         return var, P
     else:
         return var.to((u.erg/u.s/u.cm**2/u.sr)**4)
+

### 2020-02-20 paper/ms.tex
Fix previous commit
Update author order

@@
 
-\newcommand{\zst}{\ensuremath{z_{\star}}}
+\newcommand{\zv}{\ensuremath{z_{v}}}
 \newcommand{\E}[1]{\mathrm{E}[#1]}
@@
 % Keep the title short and informative.
-\title[The transition redshift as an EoR probe]{The transition redshift as a probe of reionization}
+\title[The vanishing redshift as an EoR probe]{The vanishing redshift as a probe of reionization}
 
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[A. Beane et al.]{
-Angus Beane,$^{1}$\thanks{E-mail: angus.beane@cfa.harvard.edu}
-Adam Lidz,$^{2}$
-Kana Moriwaki,$^{3}$
+\author[K. Moriwaki et al.]{
+Kana Moriwaki,$^{1}$\thanks{E-mail: kana.moriwaki@utap.phys.s.u-tokyo.ac.jp}
+Angus Beane,$^{2}$\thanks{E-mail: angus.beane@cfa.harvard.edu}
+Adam Lidz,$^{3}$
 and others
@@
 % List of institutions
-$^{1}$Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{2}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA\\
-$^{3}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan
+$^{1}$Department of Physics, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan\\
+$^{2}$Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{3}$Department of Physics \& Astronomy, University of Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA\\
 % $^{2}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Avenue, New York, NY 10010, USA\\
@@
 from being positively correlated with the density field to being negatively
-correlated. The redshift at which this occurs (the ``transition redshift'') is
+correlated. The redshift at which this occurs (the ``vanishing redshift'') is
 in principle measurable if the 21~cm field can be cross-correlated with a
 tracer of the density field (such as galaxies or a line intensity map) at that
-high redshift. Since the transition redshift is derived from a
+high redshift. Since the vanishing redshift is derived from a
 cross-correlation, it naively depends on the structure of the 21~cm field and
@@
 Kilometre Array and the Cosmic Dawn Intensity Mapper, we show that the
-transition redshift is measurable up until about $z\sim x$. Being derived from
-a cross-correlation, the transition redshift is less impacted by foreground
+vanishing redshift is measurable up until about $z\sim x$. Being derived from
+a cross-correlation, the vanishing redshift is less impacted by foreground
 contamination currently inhibiting 21~cm auto-spectrum measurements.
-Therefore, the transition redshift is an interesting probe of the early stages
+Therefore, the vanishing redshift is an interesting probe of the early stages
 of the EoR, and its detectability and interpretability deserve further study.
@@
 2014PhRvD..89b3002D, 2016ApJ...833..102B, 2017ApJ...838...65P}.
+
+Because of the difficulties in making 21~cm auto-spectrum measurements, the prospect of measuring 21~cm in cross-correlation with
 
@@
 a 21~cm, [\CII], and [\OIII] overlap \citep{2019ApJ...874..133B}. Because the
-transition redshift is typically $\z_{\star} \sim 10$, it is unclear how much
+vanishing redshift is typically $\zv \sim 10$, it is unclear how much
 metal enrichment will have occurred by this early time.
@@
 galaxies will become negatively correlated. We refer to the redshift at which
-this transition occurs at a fixed $k$ as the ``transition redshift''
-$z_\star(k)$, assuming that only one such zero exists. In other words, the
-cross-correlation at $k$ vanishes at $z=z_{\star}(k)$.
+this transition occurs at a fixed $k$ as the ``vanishing redshift''
+$\zv(k)$, assuming that only one such zero exists. In other words, the
+cross-correlation at $k$ vanishes at $z=\zv(k)$.
 
-In this work we investigate to what extent the transition redshift is
+In this work we investigate to what extent the vanishing redshift is
 dependent upon the galaxy sample used to define it. We assume a galaxy catalog
 selected using an [\OIII] emitter survey. In particular, we are interested in
-how $z_\star$ changes as we vary the parameters of the [\OIII] luminosity-mass
+how \zv{} changes as we vary the parameters of the [\OIII] luminosity-mass
 relation for a fixed halo catalog.
@@
 \section{Methods} \label{sec:methods}
-\subsection{The transition redshift} \label{ssec:ztran_def}
-The transition redshift $\zst(k)$ is defined by a field $x$ which traces the
+\subsection{The vanishing redshift} \label{ssec:ztran_def}
+The vanishing redshift $\zv(k)$ is defined by a field $x$ which traces the
 density field on large scales and the condition that
 \beq \label{eq:ztran_def}
-P_{21,x}(k, \zst(k)) \equiv 0\text{.}
+P_{21,x}(k, \zv(k)) \equiv 0\text{.}
 \eeq
-If more than one such \zst{} exists, then we choose the lowest one where
+If more than one such \zv{} exists, then we choose the lowest one where
 $P_{21,x}$ last transitioned from positive to negative.
@@
 \section{Results} \label{sec:results}
-\subsection{The transition redshift} \label{ssec:ztran_results}
+\subsection{The vanishing redshift} \label{ssec:ztran_results}
 
@@
 heating history of each model, showing the strong differences in the monopole
-signal. The transition redshift \zst{} (defined where $P_{21,\delta}(\zst{}) =
+signal. The vanishing redshift \zv{} (defined where $P_{21,\delta}(\zv{}) =
 0$) for each model is shown as a vertically dashed line. We see that models in
-which heating is more efficient have an earlier \zst{}.}
+which heating is more efficient have an earlier \zv{}.}
 \label{fig:aveTb_nf}
@@
 
-We first investigate the dependence of the transition redshift as defined by
-the halo field. Fig.~\ref{fig:ztran_vs_k} shows the transition redshift
+We first investigate the dependence of the vanishing redshift as defined by
+the halo field. Fig.~\ref{fig:ztran_vs_k} shows the vanishing redshift
 defined by the 21~cm\,--\,density cross-power spectrum (see
@@
 
-Fig.~\ref{fig:ztran_vs_k} shows that \zst{} is only weakly a function of $k$.
+Fig.~\ref{fig:ztran_vs_k} shows that \zv{} is only weakly a function of $k$.
 
@@
 \includegraphics[width=\columnwidth]{plots/ztran_vs_k.pdf}
-\caption{The transition redshift ($\zst$) as defined by cross-correlating with the
+\caption{The vanishing redshift ($\zv$) as defined by cross-correlating with the
 density field (solid lines) and all resolved halos (dashed lines, $M\gtrsim
 5\times10^9\,\Msun$), for our three different EoR models (\hot{}, \fid{}, and
-\cold{}). We see that \zst{} is only a mild function of $k$ for the three
+\cold{}). We see that \zv{} is only a mild function of $k$ for the three
 models, with slightly stronger dependence as the heating of the model
-decreases. The most dependence comes in the \cold{} model, where \zst{}
+decreases. The most dependence comes in the \cold{} model, where \zv{}
 changes by $\sim7\,\%$ from $k=0.1$ to $0.6\,\hoverMpc$. {\bf Some words for
@@
 \includegraphics[width=\columnwidth]{plots/ztran_vs_Mcut.pdf}
-\caption{The transition redshift (\zst) as defined by cross-correlating with
+\caption{The vanishing redshift (\zv) as defined by cross-correlating with
 the halo field for our three different EoR models (\hot{}, \fid{}, and
@@
 between the 21~cm field and all halos with masses $M>M_{\text{cut}}$. One can
-see that for the \fid{} and \cold{} models, \zst{} is only mildly a function
+see that for the \fid{} and \cold{} models, \zv{} is only mildly a function
 of $M_{\text{cut}}$ below a certain cut-off mass ($\sim10^{10.5}\,\Msun$ in
 both models). In other words, as long as a galaxy survey is deep enough so as
-to resolve a sufficient number of galaxies, the \zst{} is not dependent on the
+to resolve a sufficient number of galaxies, the \zv{} is not dependent on the
 depth of the survey. The \hot{} model shows more dependence, but this may be
 due to sampling noise due to the smaller number of such halos at the higher
-\zst{} typical for the \hot{} model.}
+\zv{} typical for the \hot{} model.}
 \end{figure}
@@
 \subsection{Line-intensity mapping} \label{ssec:lim}
-We now turn to understanding how \zst{} depends on the parameters of our
+We now turn to understanding how \zv{} depends on the parameters of our
 generic line-intensity mapping field: the slope ($\alpha$) and lognormal
@@
 
-In Fig.~\ref{fig:ztran_vs_alpha_sigma} we plot \zst{} as a function of each of
-these parameters\,--\,$\alpha$ and $\sigma$. We see that \zst{} is remarkably
+In Fig.~\ref{fig:ztran_vs_alpha_sigma} we plot \zv{} as a function of each of
+these parameters\,--\,$\alpha$ and $\sigma$. We see that \zv{} is remarkably
 insensitive to the value of either of these parameters, with some small
@@
 \includegraphics[width=\textwidth]{plots/ztran_vs_alpha_sigma.pdf}
-\caption{The transition redshift (\zst) defined by cross-correlating with a
+\caption{The vanishing redshift (\zv) defined by cross-correlating with a
 generic two-parameter intensity mapping field. The parameter $\alpha$ sets the
@@
 $0.52\%$ with respect to $\alpha$, and $0.070\%$, $0.10\%$, and $0.11\%$ with
-respect to $\sigma$, respectively. Clearly \zst{} varies only with the
+respect to $\sigma$, respectively. Clearly \zv{} varies only with the
 structure of the 21~cm field, and is thus an excellent probe of reionization.}
@@
 Up to this point, we have not been specific about which galactic emission line
-one might consider using to measure \zst{}\,--\,in fact, our entire formalism
+one might consider using to measure \zv{}\,--\,in fact, our entire formalism
 could be executed using a galaxy survey, if one with sufficient redshift
@@
 redshift bin of $\Delta z = 0.03$, which is smaller than the expected error we
-compute on \zst{}, and so is not an unreasonable choice. We assume a $k$-bin
+compute on \zv{}, and so is not an unreasonable choice. We assume a $k$-bin
 of fairly large width, from $k=0.1$ to $0.4\,\Mpc^{-1}$.
 
-By expanding $P_{21,\Ha}$ as a linear function about \zst{}, we can estimate the
-error on \zst{} by
+By expanding $P_{21,\Ha}$ as a linear function about \zv{}, we can estimate the
+error on \zv{} by
 \beq \label{eq:error_on_zst}
-\Var{\zst} = \left(\left.\frac{\partial P_{21,\Ha}}{\partial z}\right|_{\zst}\right)^{-2} \Var{P_{21,\Ha}}\text{,}
+\Var{\zv} = \left(\left.\frac{\partial P_{21,\Ha}}{\partial z}\right|_{\zv}\right)^{-2} \Var{P_{21,\Ha}}\text{,}
 \eeq
